### 2014-03-02 paper.tex
First page is blank

\documentclass{paper}
\usepackage{authblk}

\title{Blowship}
\author[*]{John Carlyle}
\author[**]{Morgan McDermott}
\affil[*]{University of fighitng bears}
\affil[**]{University of sillypants}

\begin{document}
\maketitle
\twocolumn
\section{Introduction}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut 
\section{Another Section} labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{document}

### 2014-03-04 paper.tex
Penguinnn

@@
 \usepackage{authblk}
+\usepackage{graphicx}
+\usepackage{wrapfig}
+\usepackage[margin=1.0in]{geometry}
 
@@
 Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut
-\section{Another Section} labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut
+\section{Privacy Goals}
+  The goal of this system is to provide an in-browser method for communicating securely between parties without massive latency or communication overhead.
+We attempt to satisfy these requirements assuming the intermediate server may be compromised.
+By communicating securely we mean specifically (using terminology from \textbf{[6]}):
+  \\\\\textbf{Communication Privacy}. Any party Eve cannot read the contents of intercepted messages sent between any two parties Alice and Bob. 
+  \\\textbf{Participant Privacy}.
+Any party Eve, cannot determine with probability $p > \epsilon$ that the two are communicating, given any $\epsilon$ chosen by Alice and Bob (with a clear lower bound of $\epsilon > 1/N$ where $N$ is the number of participants).
+The ability of multiple participants to collude and determine this with $p > \epsilon$ must be well defined.
+  \\\textbf{Destination Privacy}. Any party Eve in the network cannot determine the final destination of any party Alice's messages. This is a less stringent requirement than Participant Privacy.
+\section{PSP}
+In this section we introduce
+$P2(S2P2)^nP$, or PSP for short. PSP is an alternative to P2P protocols in which peers communicate with eachother through an alternating chain of peer-server and server-peer communications.
+\\\\
+\begin{figure}[ht]
+  \includegraphics[width=290px]{PSP.png}
+  \caption{A simple PSP communication chain}
+\end{figure}
+\\\\
+\subsection{Adversaries}
+In this context, we have several distinct types of adversaries we must consider:
+\begin{enumerate}
+  \item\textbf{Penguin.} Penguin is any Peer who can intercept and alter messages being passed through it. 
+  \item\textbf{Surge.} Surge is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
+  \item\textbf{Proletariat.} The Proletariat is a group of colluding Penguins.
+  \item\textbf{The Palace.} The Palace is a collusion of the Proletariat and Surge.
+\end{enumerate}
+\subsection{Basic Protocol}
+Assume that Alice has obtained Bob's public key and unique ID while maintaining her anonymity.
+Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge.
+
+Alice can then send a message to bob that will follow the path $A \rightarrow P_1 \rightarrow S \rightarrow ... \rightarrow S \rightarrow P_n \rightarrow B$ by sending the following message to Surge: 
+\\\\
+Let $M = E_{KRA}[  time || nonce || message ]$
+\\Let $F_{ij}[x] = E_{KUi}[ ID_j || E_{KUj}[ x ] ]$
+\\
+Alice sends: $F_{S1}[F_{S2}[...F_{nB}[ M ]]]$ to Surge.
+
+Each successive party receives a message and an ID to forward that message to, and only that party can read its message.
+Importantly, any non-colluding Penguin doesn't gain any information about the source or destination of the message it's passing along.
+
+\subsection{Security Flaws}
+Here we'll perform a simplified analysis of the security flaws of this system.
+Let $P_{AB}$ be the probability that Alice is talking to Bob. 
+\begin{enumerate}
+\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $P_1 ...
+P_n$, $Surge$ can determine that $P_{AB} > 1/(n+1) \gg 1/N$.
+This is because Surge knows that one of $A \cup \{P_1 ...
+P_n\}$ talked to Bob.
+\item\textbf{Collusion.} If there is a Proletariat of size $s$ colluding with Surge to form the Palace, then the Palace can determine on average (depending on which peers were picked), that $P_{AB} >1/(n/(N-s)+1)$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
+\item\textbf{Timing.} Even if $P_1 ...
+P_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking.
+\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases even more. 
+\end{enumerate}
+This is fairly poor security.
+If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB} > 1/6$ chance that Alice is talking to Bob.
+If $60\%$ of peers are part of the Palace, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$.
+
+\subsection{Solutions}
+To begin solving these problems, change the protocol so that any non-Penguin peer will always send two or more messages simultaneously.
+
+If we assume that there is not a Palace, then Alice needs only choose $n = log(N)$, and then Surge can only tell that $P_{AB} > 1 / 2^{log(N)} = 1/N $.
+In this way Surge gains no information about $P_{AB}$.
+If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance $< n$ from Alice, and then $P_{AB} > 1 / 2^{log(N) - 1} = 2/N$, which is still reasonable.
+\\\\
+\textbf{The Palace.} Assuming there is a Palace $S$ with $s = |S| > n$ peers, and Alice chooses her $|R| = n$ peers randomly, there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$.
+If $s = \phi*N$ peers are part of the palace, on average $E[P_{AB}] = 1 / 2^{\phi log(N)}$.
+The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Palace members as peers.
+
+\\This happens with probability $\sum\limits_{i=x}^n\phi^i$ where 
+\\ $P_{AB} = 1 / 2^{n - x} = 1 / 2^{log(N) - x} = \gamma$
+\\ $x = 2^{loglog(N)/\gamma}$
+
+\begin{figure}[ht]
+    \begin{tabular}{| l | l | l | l | l | l |}
+      \hline
+      $\phi$ & N & $E[P_{AB}]$ & x & n & $p(P_{AB} > 0.5)$ \\\hline
+      0.5 & 1000 & 0.031 & 4 & 10 & 0.12\\
+      0.5 & 10000 & 0.01 & 4 & 14 & 0.12\\
+      0.5 & 100000 & 0.003 & 5 & 17 & 0.06\\
+      \hline
+    \end{tabular}
+    \caption{Table 42.42 - Probabilities things are bad}
+\end{figure}
+
+While less than ideal this is not bad. The chance that Surge, having $50\%$ of peers colluding with him, can tell that Alice is talking to Bob with probability $> 0.5$ is only $12\%$. 
+\\\\
+\textbf{The Dictatorship.}
+Unfortunately, if peers discover eachother through Surge, he can ensure that $\phi = 1$ by only sharing information about peers who are part of the Palace. 
+\\\\
+This is still a problem.
 \end{document}

### 2014-03-04 paper.tex
Penguinnn

@@
 Each successive party receives a message and an ID to forward that message to, and only that party can read its message.
-Importantly, any non-colluding Penguin doesn't gain any information about the source or destination of the message it's passing along.
+Importantly, any Penguin or Proletariat without collusion from Surge doesn't gain any information about the source or destination of the message it's passing along.
+\\\\
+Note that Surge can't track a message by its contents, since it gets decrypted and changed by each successive peer.
 
@@
 \item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $P_1 ...
-P_n$, $Surge$ can determine that $P_{AB} > 1/(n+1) \gg 1/N$.
+P_n$, $Surge$ can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$.
 This is because Surge knows that one of $A \cup \{P_1 ...
 P_n\}$ talked to Bob.
-\item\textbf{Collusion.} If there is a Proletariat of size $s$ colluding with Surge to form the Palace, then the Palace can determine on average (depending on which peers were picked), that $P_{AB} >1/(n/(N-s)+1)$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
+\item\textbf{Collusion.} If there is a Proletariat of size $s$ colluding with Surge to form the Palace, then the Palace can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
 \item\textbf{Timing.} Even if $P_1 ...
@@
 
-If we assume that there is not a Palace, then Alice needs only choose $n = log(N)$, and then Surge can only tell that $P_{AB} > 1 / 2^{log(N)} = 1/N $.
-In this way Surge gains no information about $P_{AB}$.
-If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance $< n$ from Alice, and then $P_{AB} > 1 / 2^{log(N) - 1} = 2/N$, which is still reasonable.
+If we assume that there is not a Palace, then Alice needs only choose $n = O(log(N))$, and then Surge can only tell that $P_{AB} = 2^{-O(log(N))} \approx 1/N $.
+If every node sends 2 messages at once, and her message passes through $O(log(N))$ nodes, then there are $O(2^n)$ possible routes her message could have taken and hopefully $O(2^n)$ possible destinations.
+The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose.
+If every node has an average unique branching factor of $z$ rather than $2$, we can use $n = y log(N)$ and then: $z^{-ylog(N)} = 1/N$ and so $y = 1/log(z) \Rightarrow n = log(N)/log(z)$
+
+\\\\In this way Surge gains no information about $P_{AB}$.
+If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance $< n$ from Alice, and then $P_{AB} = 2^{-(log(N)-1)} = 2/N$, which is still reasonable.
 \\\\
 \textbf{The Palace.} Assuming there is a Palace $S$ with $s = |S| > n$ peers, and Alice chooses her $|R| = n$ peers randomly, there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$.
-If $s = \phi*N$ peers are part of the palace, on average $E[P_{AB}] = 1 / 2^{\phi log(N)}$.
+If $s = \phi*N$ peers are part of the palace, on average $E[P_{AB}] = 2^{-\phi log(N)}$.
 The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Palace members as peers.
@@
 \\This happens with probability $\sum\limits_{i=x}^n\phi^i$ where 
-\\ $P_{AB} = 1 / 2^{n - x} = 1 / 2^{log(N) - x} = \gamma$
+\\ $P_{AB} = 2^{-(n - x)} = 2^{-(log(N) - x)} = \gamma$
 \\ $x = 2^{loglog(N)/\gamma}$

### 2014-03-04 paper.tex
Bib

@@
 \usepackage{wrapfig}
+\usepackage{cite}
 \usepackage[margin=1.0in]{geometry}
@@
 Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut
+\section{Previous Work}
+There has been a plethora of original work and refinement in the area of anonymous internet communication. Broadly categorized, these include:
+\begin{enumerate}
+  \item Mixes \cite{chaum-mix} 
+  \item Onion routing \cite{onion-discex00}
+  \item Freedom (wtf) [z]
+\end{enumerate}
 \section{Privacy Goals}
@@
   \\\textbf{Participant Privacy}.
+This is also called \textbf{Unobservability} and \textbf{Untraceability}.
 Any party Eve, cannot determine with probability $p > \epsilon$ that the two are communicating, given any $\epsilon$ chosen by Alice and Bob (with a clear lower bound of $\epsilon > 1/N$ where $N$ is the number of participants).
@@
 $P2(S2P2)^nP$, or PSP for short. PSP is an alternative to P2P protocols in which peers communicate with eachother through an alternating chain of peer-server and server-peer communications.
-\\\\
+
 \begin{figure}[ht]
@@
 \end{figure}
-\\\\
-\subsection{Adversaries}
-In this context, we have several distinct types of adversaries we must consider:
-\begin{enumerate}
-  \item\textbf{Penguin.} Penguin is any Peer who can intercept and alter messages being passed through it. 
-  \item\textbf{Surge.} Surge is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
-  \item\textbf{Proletariat.} The Proletariat is a group of colluding Penguins.
-  \item\textbf{The Palace.} The Palace is a collusion of the Proletariat and Surge.
-\end{enumerate}
+
 \subsection{Basic Protocol}
@@
 Note that Surge can't track a message by its contents, since it gets decrypted and changed by each successive peer. 
-
+\\\\
+In this system, peers operate exactly as MIXes in the literature \cite{chaum-mix} .
+That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[TODO]]], as well (as we will discuss) by reordering and batching messages.
+\subsection{Adversaries}
+In this context, we have several distinct types of adversaries we must consider:
+\begin{enumerate}
+  \item\textbf{Penguin.} Penguin is any Peer who can intercept and alter messages being passed through it. 
+  \item\textbf{Surge.} Surge is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
+  \item\textbf{Proletariat.} The Proletariat is a group of colluding Penguins.
+  \item\textbf{The Palace.} The Palace is a collusion of the Proletariat and Surge.
+\end{enumerate}
 \subsection{Security Flaws}
-Here we'll perform a simplified analysis of the security flaws of this system.
+Here we'll perform a simplified analysis of the security flaws of the basic, naive system described so far. 
 Let $P_{AB}$ be the probability that Alice is talking to Bob. 
@@
 The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose.
-If every node has an average unique branching factor of $z$ rather than $2$, we can use $n = y log(N)$ and then: $z^{-ylog(N)} = 1/N$ and so $y = 1/log(z) \Rightarrow n = log(N)/log(z)$
+If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$.
 
@@
 This is still a problem.
+\bibliography{paper.bib}
+\bibliographystyle{plain}
 \end{document}

### 2014-03-04 paper.tex
Omg errors

@@
 \begin{figure}[ht]
-  \includegraphics[width=290px]{PSP.png}
+  \includegraphics[width=230px]{PSP.png}
   \caption{A simple PSP communication chain}
@@
 Alice can then send a message to bob that will follow the path $A \rightarrow P_1 \rightarrow S \rightarrow ... \rightarrow S \rightarrow P_n \rightarrow B$ by sending the following message to Surge: 
-\\\\
+\\
 Let $M = E_{KRA}[  time || nonce || message ]$
@@
 Importantly, any Penguin or Proletariat without collusion from Surge doesn't gain any information about the source or destination of the message it's passing along.
-\\\\
+\\
 Note that Surge can't track a message by its contents, since it gets decrypted and changed by each successive peer. 
-\\\\
+\\
 In this system, peers operate exactly as MIXes in the literature \cite{chaum-mix} .
@@
 If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$.
-
-\\\\In this way Surge gains no information about $P_{AB}$.
+\\In this way Surge gains no information about $P_{AB}$.
 If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance $< n$ from Alice, and then $P_{AB} = 2^{-(log(N)-1)} = 2/N$, which is still reasonable.
-\\\\
+\\
 \textbf{The Palace.} Assuming there is a Palace $S$ with $s = |S| > n$ peers, and Alice chooses her $|R| = n$ peers randomly, there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$.
@@
 The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Palace members as peers.
-
 \\This happens with probability $\sum\limits_{i=x}^n\phi^i$ where 
@@
 While less than ideal this is not bad. The chance that Surge, having $50\%$ of peers colluding with him, can tell that Alice is talking to Bob with probability $> 0.5$ is only $12\%$. 
-\\\\
+\\
 \textbf{The Dictatorship.}
 Unfortunately, if peers discover eachother through Surge, he can ensure that $\phi = 1$ by only sharing information about peers who are part of the Palace. 
-\\\\
+\\
 This is still a problem.

### 2014-03-05 paper.tex
Peers as mixes

@@
 \subsection{Solutions}
-To begin solving these problems, change the protocol so that any non-Penguin peer will always send two or more messages simultaneously.
+To begin solving these problems, change the protocol so that any non-Penguin peer will always wait until it can send two or more messages simultaneously.
+This is equivilant to turning each peer into a 2-Threshold mix.
+\cite{TODO}
 
@@
 This is still a problem.
+\subsection{Peers as Mixes}
+As previously discussed, peers act as mixes in this system - inheriting both their benefits and vulnerabilities.
+Many types of mixes have been developed, and Serjantov \cite{trickle02} has compiled common attacks and solutions.
+\paragraph{}A mix holds on to incoming messages until its \textbf{flush function} is satisfied, then it forwards some subset of its collected messages.
+Common attacks are variants of the $n - 1$ or $flooding$ attack, in which an attacker fills the mix with its own fake messages and then sends the 1 message he wishes to track.
+\paragraph{} All known mix types are vulnerable to such exact attacks \cite{trickle02} -  attacks that allow an attacker to know whether his attack was successful or not and try again if not.
+Since in our threat model Surge has complete access to the message history of each peer as well as the ability to delay and insert as many messages as he desires, trying to prevent these attacks by implementing a better flush function is even more futile.
+\paragraph{} Fortunately, due to the nature of this system we can provide almost complete protection with \textbf{cover traffic} \cite{trickle02}, or having each peer send dummy messages along with the messages it's forwarding.
+If done correctly in this model, a peer should at minimum send one dummy message along with every real message, maintaining a branching factor of two at every hop.
+Typically providing complete protection with cover traffic is difficult - it requires the mix to choose dummy message recipients uniformally from all users.
+In our system, however, randomly and anonymously choosing other online peers is designed to be efficient.
+\paragraph{} It would also be possible to use inter-mix detours\cite{TODO}, or having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack.
+However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system.
+
 \bibliography{paper.bib}

### 2014-03-05 paper.tex
Formatting

@@
 Importantly, any Penguin or Proletariat without collusion from Surge doesn't gain any information about the source or destination of the message it's passing along.
-\\
+
 Note that Surge can't track a message by its contents, since it gets decrypted and changed by each successive peer.
-\\
+
 In this system, peers operate exactly as MIXes in the literature \cite{chaum-mix} .
@@
 If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$.
-\\In this way Surge gains no information about $P_{AB}$.
+
+In this way Surge gains no information about $P_{AB}$.
 If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance $< n$ from Alice, and then $P_{AB} = 2^{-(log(N)-1)} = 2/N$, which is still reasonable.
-\\
-\textbf{The Palace.} Assuming there is a Palace $S$ with $s = |S| > n$ peers, and Alice chooses her $|R| = n$ peers randomly, there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$.
+
+\paragraph{The Palace.} Assuming there is a Palace $S$ with $s = |S| > n$ peers, and Alice chooses her $|R| = n$ peers randomly, there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$.
 If $s = \phi*N$ peers are part of the palace, on average $E[P_{AB}] = 2^{-\phi log(N)}$.
 The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Palace members as peers.
-\\This happens with probability $\sum\limits_{i=x}^n\phi^i$ where 
+
+This happens with probability $\sum\limits_{i=x}^n\phi^i$ where 
 \\ $P_{AB} = 2^{-(n - x)} = 2^{-(log(N) - x)} = \gamma$
@@
 While less than ideal this is not bad. The chance that Surge, having $50\%$ of peers colluding with him, can tell that Alice is talking to Bob with probability $> 0.5$ is only $12\%$.
-\\
-\textbf{The Dictatorship.}
+
+\paragraph{The Dictatorship.}
 Unfortunately, if peers discover eachother through Surge, he can ensure that $\phi = 1$ by only sharing information about peers who are part of the Palace.
-\\
+
 This is still a problem.
@@
 Many types of mixes have been developed, and Serjantov \cite{trickle02} has compiled common attacks and solutions.
-\paragraph{}A mix holds on to incoming messages until its \textbf{flush function} is satisfied, then it forwards some subset of its collected messages.
+A mix holds on to incoming messages until its \textbf{flush function} is satisfied, then it forwards some subset of its collected messages.
 Common attacks are variants of the $n - 1$ or $flooding$ attack, in which an attacker fills the mix with its own fake messages and then sends the 1 message he wishes to track.
-\paragraph{} All known mix types are vulnerable to such exact attacks \cite{trickle02} -  attacks that allow an attacker to know whether his attack was successful or not and try again if not.
+
+All known mix types are vulnerable to such exact attacks \cite{trickle02} -  attacks that allow an attacker to know whether his attack was successful or not and try again if not.
 Since in our threat model Surge has complete access to the message history of each peer as well as the ability to delay and insert as many messages as he desires, trying to prevent these attacks by implementing a better flush function is even more futile.
-\paragraph{} Fortunately, due to the nature of this system we can provide almost complete protection with \textbf{cover traffic} \cite{trickle02}, or having each peer send dummy messages along with the messages it's forwarding.
+
+Fortunately, due to the nature of this system we can provide almost complete protection with \textbf{cover traffic} \cite{trickle02}, or having each peer send dummy messages along with the messages it's forwarding.
 If done correctly in this model, a peer should at minimum send one dummy message along with every real message, maintaining a branching factor of two at every hop.
@@
 In our system, however, randomly and anonymously choosing other online peers is designed to be efficient.
-\paragraph{} It would also be possible to use inter-mix detours\cite{TODO}, or having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack.
+
+It would also be possible to use inter-mix detours\cite{TODO}, or having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack.
 However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system.

### 2014-03-09 paper.tex
Fleshy flesh

@@
 \usepackage{cite}
+\usepackage{relsize}
 \usepackage[margin=1.0in]{geometry}
 
-\title{Blowship}
+\title{Blowship - Anonymous Communication via a Central Server}
 \author[*]{John Carlyle}
@@
 \twocolumn
+
+\section*{Abstract} 
+  Many systems have been developed that preserve the anonymity of the sender and receiver of data.
+These systems are typically decentralized, routing messages through some series of trusted or untrusted peers and servers.
+
+In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized p2p protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication.
 \section{Introduction}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut
+
 \section{Previous Work}
-There has been a plethora of original work and refinement in the area of anonymous internet communication. Broadly categorized, these include:
-\begin{enumerate}
-  \item Mixes \cite{chaum-mix} 
-  \item Onion routing \cite{onion-discex00}
-  \item Freedom (wtf) [z]
-\end{enumerate}
+\paragraph{Mixes.} Mixes are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies.
+Mixes have seen wide use since Chaum first introduced them in his 1981 paper \cite{chaum-mix}.
+They have been used in systems such as MixMinion\cite{minion-design} to anonymously send and receive email.
+[TODO: more explanation]
+\paragraph{Onion Routing.} \cite{onion-discex00}
+\paragraph{Nym systems.} Pseudonymous message delivery systems enable users to send messages from a \textit{nym} (pseudonym) that cannot be traced back to their true identity.
+Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient - which is what we are attempting to develop in this paper.
+\paragraph{Private Information Retrieval.} PIR has been used to facilitate anonymous communication in a variety of ways.
+The Pynchon Gate \cite{wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees.
+
+\section{Measuring Anonymity}
+  \textit{Anonymity sets}, introduced by Chaum in his Dining Cryptographers paper \cite{chaum-dc}, are widely used to analyze the anonymity provided by various p2p privacy schemes.
+Given a message and whatever information an attacker has obtained, the anonymity set for that message is the set of users who could have sent it.
+An anonymity set of size 1 means that the attacker knows exactly who sent the message.
+
+This measure fails to capture some of the information gathered by the attacker.
+If, for instance, certain members of an anonymity set are more likely to have sent the message (which is never the case in Chaum's DC networks \cite{chaum-dc}), this information is not captured by the size of the anonymity set.
+
+To solve this problem, Diaz \cite{Diaz02} and Serjantov \cite{Serj02} independently developed almost identical solutions.
+Their idea is this: given a message, consider the probability distribution of its senders.
+The entropy of this probability distribution then represents the number of bits an attacker still needs to obtain in order to identify the sender of the message.
+
+Serjantov \cite{Serj02} calls this measure the \textit{size} $S$ of the anonymity probability distribution.
+Given $U$ is the set of all users, and $p_u$ is the probability that $u \in U$ sent the message under its probability distribution for users, then the $size$ of the probability distribution is:
+
+\begin{center}
+$ S = - \mathlarger{\sum}\limits_{u \in U} p_u $log$_2(p_u)$
+\end{center}
+
+For example, if we give one user a probability $1$ of sending the message, all other users have probability 0, and $S = -(1 * 0) = 0$, meaning the attacker needs no more information to identify the user.
+
 \section{Privacy Goals}
-  The goal of this system is to provide an in-browser method for communicating securely between parties without massive latency or communication overhead.
+  The goal of this system is to provide a method for communicating securely between parties through a central server with low latency and low communication overhead.
 We attempt to satisfy these requirements assuming the intermediate server may be compromised.
@@
 This is also called \textbf{Unobservability} and \textbf{Untraceability}.
-Any party Eve, cannot determine with probability $p > \epsilon$ that the two are communicating, given any $\epsilon$ chosen by Alice and Bob (with a clear lower bound of $\epsilon > 1/N$ where $N$ is the number of participants).
+Any party Eve cannot determine with probability $p > \epsilon$ that Alice and Bob are communicating, given any chosen $\epsilon$ (with a clear lower bound of $\epsilon > 1/N$ where $N$ is the number of participants).
 The ability of multiple participants to collude and determine this with $p > \epsilon$ must be well defined.
   \\\textbf{Destination Privacy}. Any party Eve in the network cannot determine the final destination of any party Alice's messages. This is a less stringent requirement than Participant Privacy.
-\section{PSP}
-In this section we introduce
-$P2(S2P2)^nP$, or PSP for short. PSP is an alternative to P2P protocols in which peers communicate with eachother through an alternating chain of peer-server and server-peer communications.
+\section{Central Server Communication}
+ The majority of research into anonymous communication uses decentralized p2p networks.
+In some cases, however, it is necessary (and possibly beneficial) to communicate through a central server.
+Many of the developed p2p techniques can be adapted by using a pseudo-p2p protocol, by having peers communicate with each other indirectly through the central server.
+
+ In p2p protocols, delivering a message via a chain of peers or servers is common: Mix-based systems use cascades and mix networks, onion-based systems create circuits, etc.
+In this system we'll use the onion routing terminology and call the chain of peers a message passes through a $circuit$.
 
@@
   \includegraphics[width=230px]{PSP.png}
-  \caption{A simple PSP communication chain}
+  \caption{A simple pseudo-p2p circuit}
 \end{figure}
@@
 Here we'll perform a simplified analysis of the security flaws of the basic, naive system described so far. 
-Let $P_{AB}$ be the probability that Alice is talking to Bob. 
+Let $P_{AB}$ be the probability that Alice sent a given message that was delivered to to Bob. 
 \begin{enumerate}
@@
 P_n\}$ talked to Bob.
-\item\textbf{Collusion.} If there is a Proletariat of size $s$ colluding with Surge to form the Palace, then the Palace can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
+\item\textbf{Collusion.} If  $s$ peers collude with Surge to form the Palace, then the Palace can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
 \item\textbf{Timing.} Even if $P_1 ...
@@
 \item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases even more. 
+\item\textbf{Man in the Middle.} If Alice acquries Bob's public key from Surge (and vice-versa), there's nothing to stop Surge from mounting a Man in the Middle attack given this simple model. 
 \end{enumerate}
@@
 
-If we assume that there is not a Palace, then Alice needs only choose $n = O(log(N))$, and then Surge can only tell that $P_{AB} = 2^{-O(log(N))} \approx 1/N $.
-If every node sends 2 messages at once, and her message passes through $O(log(N))$ nodes, then there are $O(2^n)$ possible routes her message could have taken and hopefully $O(2^n)$ possible destinations.
+If we assume that there is not a Palace, then Alice needs only choose $n = log(N)$, If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = N$ possible messages that Alice sent, and hopefully $N$ possible destinations.
 The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose.
 If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$.
+Then, the $size$ of Alice's anonymity probability distribution is $\approx 1$ since the sender probabilities are roughly uniform.
 
-In this way Surge gains no information about $P_{AB}$.
-If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance $< n$ from Alice, and then $P_{AB} = 2^{-(log(N)-1)} = 2/N$, which is still reasonable.
+In this way Surge gains no information about the sender of the message.
+If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance $< n$ from Alice, and then $P_{AB} = 2^{-(log(N)-1)} = 2/N$, and $S = - \frac{1}{4} log(\frac{1}{2N})$ which is still reasonable, though Alice could compensate by randomly choosing the length of her circuit.
 
-\paragraph{The Palace.} Assuming there is a Palace $S$ with $s = |S| > n$ peers, and Alice chooses her $|R| = n$ peers randomly, there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$.
+\subsection{The Palace} Assuming the set $S$ peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$.
 If $s = \phi*N$ peers are part of the palace, on average $E[P_{AB}] = 2^{-\phi log(N)}$.
@@
 
-\paragraph{The Dictatorship.}
-Unfortunately, if peers discover eachother through Surge, he can ensure that $\phi = 1$ by only sharing information about peers who are part of the Palace.
+TODO: Apply PIR to obtain security guarantees even when $R \subset S$
 
-This is still a problem.
+\subsection{Peer Discovery}
+Unfortunately, if peers discover eachother through Surge, he can ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).
+
+This is a common problem in Onion routing schemes like Tor, as well as Mix networks.
+If directory servers collude with some routing servers, they can choose to only broadcast the existence of the compromised routing servers.
+
+MixMinion \cite{minion-design} solves these problems by having a small group of directory servers that only update nightly, having servers sign each other's directories, and ensuring that users download entire directories.
+These solutions are not feasible in our case since the set of online users is constantly in flux, and is likely to be too large to be sent to every user.
+Tor \cite{tor-design} likewise has a small number of trusted directory servers that share infrequently updated, signed directories.
+
+\subsection{Man in the Middle.} If both Alice and Bob are online, then they could use Diffie Hellman to ensure that Surge isn't acting as a Man in the middle.
+However, we'd like to allow offline delivery of messages.
+
+This requires some form of web of trust, or some means of verifying public keys without trusting Surge.
+
 \subsection{Peers as Mixes}
@@
 However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system.
-
+\section{Applying PIR}
 \bibliography{paper.bib}

### 2014-03-10 paper.tex
PIR stuffs

@@
 They have been used in systems such as MixMinion\cite{minion-design} to anonymously send and receive email.
-[TODO: more explanation]
-\paragraph{Onion Routing.} \cite{onion-discex00}
-\paragraph{Nym systems.} Pseudonymous message delivery systems enable users to send messages from a \textit{nym} (pseudonym) that cannot be traced back to their true identity.
+Onion routing systems such as Tor \cite{tor-design} use series of mixes as proxies for web data.
+
+\paragraph{Nym systems.} Pseudonymous message delivery systems enable users to send and receive messages with a \textit{nym} (pseudonym) that cannot be traced back to their true identity.
 Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient - which is what we are attempting to develop in this paper.
@@
 The Pynchon Gate \cite{wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees.
+Tor-PIR \cite{TODO} uses PIR to distribute information about servers without forcing users to download the entire directory.
 
@@
 However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system.
+
 \section{Applying PIR}
+An obvious way to utilize PIR for anonymous communication is as a ``Dead Drop''.
+If we have a PIR server Charlie, Alice could write her messages to block $i$ in Charlie's PIR database, then bob could request block $i$ anonymously.
+This could enable us to increase the size of Alice's anonymity set (retaining a uniform distribution of probabilities, as well) while reducing our circuit length significantly.
+
+There are several problems with this configuration, however.
+
+First, Alice must communicate Charlie's ID and $i$ to bob anonymously. This could happen via the pseudo-p2p protocol as above.
+
+Second, Alice and Bob both start talking to Charlie around the same time.
+If Charlie suspects Alice and Bob are talking to eachother, he can easily create a fake PIR database for all of Alice's inserts and all of Bob's retrievals, and if they continue to communicate normally he has found a connection.
+
+\subsection{Sliding-Window PIR}
+To Prevent correlation between the Alice-Charlie and Bob-Charlie communication start times
+
+\section{Future Work}
+\begin{enumerate}
+  \item \textbf{Pseudonymity.} Allow for parties to communicate securely without knowing eachother's identities.
+  \item \textbf{Faster circuits.} Like Tor, we could use layers of symmetric encryption between successive pairs of peers in a circuit.
+Using a public/symmetric system like Tor could help with pseudonymity as well.
+  \item \textbf{DoS.} We'd like to prevent DoS attacks by requiring some proof of work etc for messages being sent. 
+\end{enumerate}
+
+\newpage
+
 \bibliography{paper.bib}

### 2014-03-10 paper.tex
Im sure there are some changes

@@
 \section*{Abstract} 
-  Many systems have been developed that preserve the anonymity of the sender and receiver of data.
+  Mzany systems have been developed that preserve the anonymity of the sender and receiver of data.
 These systems are typically decentralized, routing messages through some series of trusted or untrusted peers and servers.
@@
 
- In p2p protocols, delivering a message via a chain of peers or servers is common: Mix-based systems use cascades and mix networks, onion-based systems create circuits, etc.
-In this system we'll use the onion routing terminology and call the chain of peers a message passes through a $circuit$.
+ In p2p protocols, delivering a message via a chain of peers or servers is a standard method to achieve anonymity.
+In this system we'll use terminology from Tor and call the chain of peers a message passes through a $circuit$.
+A pseudo-p2p circuit then consists of an alternating chain of peer-server and server-peer communications.
 
@@
 Fortunately, due to the nature of this system we can provide almost complete protection with \textbf{cover traffic} \cite{trickle02}, or having each peer send dummy messages along with the messages it's forwarding.
-If done correctly in this model, a peer should at minimum send one dummy message along with every real message, maintaining a branching factor of two at every hop.
+A peer will at minimum send one dummy message along with every real message, maintaining a branching factor greater than two at every hop.
 Typically providing complete protection with cover traffic is difficult - it requires the mix to choose dummy message recipients uniformally from all users.
@@
 
-It would also be possible to use inter-mix detours\cite{TODO}, or having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack.
+It would also be possible to use inter-mix detours\cite{TODO}, having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack.
 However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system.
@@
 \section{Future Work}
-\begin{enumerate}
-  \item \textbf{Pseudonymity.} Allow for parties to communicate securely without knowing eachother's identities.
-  \item \textbf{Faster circuits.} Like Tor, we could use layers of symmetric encryption between successive pairs of peers in a circuit.
+\begin{description}
+  \item[Pseudonymity.] Allow for parties to communicate securely without knowing eachother's identities.
+  \item[Faster circuits.] Like Tor, we could use layers of symmetric encryption between successive pairs of peers in a circuit.
 Using a public/symmetric system like Tor could help with pseudonymity as well.
-  \item \textbf{DoS.} We'd like to prevent DoS attacks by requiring some proof of work etc for messages being sent. 
-\end{enumerate}
+  \item[DoS.] We'd like to prevent DoS attacks by requiring some proof of work etc for messages being sent.
+\end{description}
 

### 2014-03-10 paper.tex
Falling balls

@@
 
+\subsection{Peer Discovery & MITM brainstorming}
+
+Lying about who's online - If you want to send a message to a real node ``B'' but B is not listed as online, you won't send a message.
+However, if he lists ``B'' as online, ``B'' can be used to route messages validly by everyone.
+
+Chain verification - Keep a web of trust with the length of the path to a person inversely proportional to how trusted they are.
+Share web of trust with those we communicate with - only share nodes with a certain level of trust, and then trust nodes discovered this way with diminished trust.
+
+If initial trust is only spread through person to person contact, then assigning negative trust is valuable because it reduces the value of colluding human nodes.
+
+* Have nodes sign messages as they pass through, so that the path can be tested/verified.
+
 \subsection{Peer Discovery}
@@
 This requires some form of web of trust, or some means of verifying public keys without trusting Surge.
+
+Users should maintain a list of known keys to make stuff good.
 

### 2014-03-11 paper.tex
Fixed errors

@@
-\documentclass{paper}
+\documentclass[twocolumn]{paper}
+\usepackage{comment}
 \usepackage{authblk}
@@
 \author[**]{Morgan McDermott}
-\affil[*]{University of fighitng bears}
-\affil[**]{University of sillypants}
+\affil[*]{University of angry bees}
+\affil[**]{University of flightless dragons}
 
@@
 \maketitle
-\twocolumn
 
 \section*{Abstract} 
-  Mzany systems have been developed that preserve the anonymity of the sender and receiver of data.
+  Many systems have been developed that preserve the anonymity of the sender and receiver of data.
 These systems are typically decentralized, routing messages through some series of trusted or untrusted peers and servers.
@@
 In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized p2p protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication.
+The primary reason behind a centeral server is to have a browser based service which needs a server to initialze the peer to peer network.
 \section{Introduction}
@@
 In this system, peers operate exactly as MIXes in the literature \cite{chaum-mix} .
-That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[TODO]]], as well (as we will discuss) by reordering and batching messages.
+That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[soething]]], as well (as we will discuss) by reordering and batching messages.
 \subsection{Adversaries}
@@
 
+\begin{comment}
 TODO: Apply PIR to obtain security guarantees even when $R \subset S$
+\end{comment}
 
-\subsection{Peer Discovery & MITM brainstorming}
+\subsection{Peer Discovery and MITM brainstorming}
 

### 2014-03-11 paper.tex
Intro

@@
 
-\title{Blowship - Anonymous Communication via a Central Server}
+\title{Blowship - Untraceable Instantaneous Message Transfer via a Central Server}
 \author[*]{John Carlyle}
@@
 The primary reason behind a centeral server is to have a browser based service which needs a server to initialze the peer to peer network.
+
 \section{Introduction}
 
+Traditional cryptography obsucres the message being sent from one party to another.
+This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: who the message is being sent to.
+Much work has been done to build networks that can obscure message passing by esentially mixing the messages around in a large group of peers in such a way that a peer in the network, or even a large group of peers cannot figure out where the message is going to end up.
+Many of these system rely upon the fact that the user is accessing a constantly avaible resource, such as with tor\cite{tor}, or in the case of email one can wait as long as nessesary for a message to be read by the user on the other end.
+
+we are presenting to the reader is Untraceable Instantaneous Messaging, via a central server.
+Our system of message passing is initiated by the browser, allowing a person to browse to one central location and conveneintly use this service.
+The central server is primarily used as an entrypoint into a network of peers.
+The peers are used to obsfucate who is sending messages to whom, allowing the clients to communicate with both private content, all in as close to real time as possible given the constraints of the algorithms being used.
+
 \section{Previous Work}
-\paragraph{Mixes.} Mixes are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies.
+\begin{description}
+\item[Mixes] Mixes are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies.
 Mixes have seen wide use since Chaum first introduced them in his 1981 paper \cite{chaum-mix}.
@@
 
-\paragraph{Nym systems.} Pseudonymous message delivery systems enable users to send and receive messages with a \textit{nym} (pseudonym) that cannot be traced back to their true identity.
+\item[Nym systems] Pseudonymous message delivery systems enable users to send and receive messages with a \textit{nym} (pseudonym) that cannot be traced back to their true identity.
 Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient - which is what we are attempting to develop in this paper.
-\paragraph{Private Information Retrieval.} PIR has been used to facilitate anonymous communication in a variety of ways.
+
+\item[Private Information Retrieval] PIR has been used to facilitate anonymous communication in a variety of ways.
 The Pynchon Gate \cite{wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees.
 Tor-PIR \cite{TODO} uses PIR to distribute information about servers without forcing users to download the entire directory.
+
+\end{description}
 
@@
 
-\subsection{Sliding-Window PIR}
-To Prevent correlation between the Alice-Charlie and Bob-Charlie communication start times
-
 \section{Future Work}

### 2014-03-11 paper.tex
fiddled with better future stuff

@@
   \item[Pseudonymity.] Allow for parties to communicate securely without knowing eachother's identities.
+Currently our system relys heavily (at least when a person first enters the network) on the fact that the person initiating the communication knows the person's key with whom he wants to communciate.
+
   \item[Faster circuits.] Like Tor, we could use layers of symmetric encryption between successive pairs of peers in a circuit.
 Using a public/symmetric system like Tor could help with pseudonymity as well.
-  \item[DoS.] We'd like to prevent DoS attacks by requiring some proof of work etc for messages being sent.
+Currently we are doing a lot of public/private key encryption which is slow.
+
+  \item[DoS.] We would like to address the issue of DoS attacks against networks by requiring messages to be accompanied by a proof of work.
+This would allow us to require that the messages being sent are by computers that are also helping to suport the network.
 \end{description}

### 2014-03-12 paper.tex
Updated stuff

@@
 \usepackage{authblk}
+\usepackage{tikz}
 \usepackage{graphicx}
@@
 
-In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized p2p protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication.
+In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized peer-to-peer (p2p) protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication.
 The primary reason behind a centeral server is to have a browser based service which needs a server to initialze the peer to peer network.
@@
 Much work has been done to build networks that can obscure message passing by esentially mixing the messages around in a large group of peers in such a way that a peer in the network, or even a large group of peers cannot figure out where the message is going to end up.
-Many of these system rely upon the fact that the user is accessing a constantly avaible resource, such as with tor\cite{tor}, or in the case of email one can wait as long as nessesary for a message to be read by the user on the other end.
+Many of these system rely upon the fact that the user is accessing a constantly avaible resource, such as with tor\cite{tor-design}, or in the case of email one can wait as long as nessesary for a message to be read by the user on the other end.
 
@@
 \item[Private Information Retrieval] PIR has been used to facilitate anonymous communication in a variety of ways.
-The Pynchon Gate \cite{wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees.
+The Pynchon Gate \cite{sassaman:wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees.
 Tor-PIR \cite{TODO} uses PIR to distribute information about servers without forcing users to download the entire directory.
@@
 \begin{figure}[ht]
-  \includegraphics[width=230px]{PSP.png}
+\begin{center}
+\begin{tikzpicture}[scale=0.2]
+\tikzstyle{every node}+=[inner sep=0pt]
+\draw [black] (15.3,-22.1) circle (3);
+\draw (15.3,-22.1) node {$Peer_a$};
+\draw [black] (22.7,-22.1) circle (3);
+\draw (22.7,-22.1) node {$S_1$};
+\draw [black] (30,-22.1) circle (3);
+\draw (30,-22.1) node {$Peer_b$};
+\draw [black] (37.2,-22.1) circle (3);
+\draw (37.2,-22.1) node {$S_2$};
+\draw [black] (44.5,-22.1) circle (3);
+\draw (44.5,-22.1) node {$Peer_c$};
+\draw [black] (18.3,-22.1) -- (19.7,-22.1);
+\fill [black] (19.7,-22.1) -- (18.9,-21.6) -- (18.9,-22.6);
+\draw [black] (25.7,-22.1) -- (27,-22.1);
+\fill [black] (27,-22.1) -- (26.2,-21.6) -- (26.2,-22.6);
+\draw [black] (33,-22.1) -- (34.2,-22.1);
+\fill [black] (34.2,-22.1) -- (33.4,-21.6) -- (33.4,-22.6);
+\draw [black] (40.2,-22.1) -- (41.5,-22.1);
+\fill [black] (41.5,-22.1) -- (40.7,-21.6) -- (40.7,-22.6);
+\end{tikzpicture}
+\end{center}
   \caption{A simple pseudo-p2p circuit}
@@
 
+\subsection{Adversaries}
+In this context, we have several distinct types of adversaries we must consider:
+\begin{description}
+\item[Penguin] 
+  is any Peer who can intercept any messages and modify the content of that message.
+\item[Surge] 
+   is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
+\item[Proletariat] 
+  is a group of colluding Penguins.
+\item[The Fort] 
+  is Surge and penguins colluding. 
+\end{description}
+
 \subsection{Basic Protocol}
 Assume that Alice has obtained Bob's public key and unique ID while maintaining her anonymity.
+This could be done using a public keyserver of some kind, or perhaps they have exchanged keys in advance through some other channel.
 Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge.
@@
 That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[soething]]], as well (as we will discuss) by reordering and batching messages.
-\subsection{Adversaries}
-In this context, we have several distinct types of adversaries we must consider:
-\begin{enumerate}
-  \item\textbf{Penguin.} Penguin is any Peer who can intercept and alter messages being passed through it. 
-  \item\textbf{Surge.} Surge is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
-  \item\textbf{Proletariat.} The Proletariat is a group of colluding Penguins.
-  \item\textbf{The Palace.} The Palace is a collusion of the Proletariat and Surge.
-\end{enumerate}
 \subsection{Security Flaws}
@@
 P_n\}$ talked to Bob.
-\item\textbf{Collusion.} If  $s$ peers collude with Surge to form the Palace, then the Palace can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
+\item\textbf{Collusion.} If  $s$ peers collude with Surge to form the Fort, then the Fort can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
 \item\textbf{Timing.} Even if $P_1 ...
@@
 If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB} > 1/6$ chance that Alice is talking to Bob.
-If $60\%$ of peers are part of the Palace, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$.
+If $60\%$ of peers are part of the Fort, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$.
 
@@
 
-If we assume that there is not a Palace, then Alice needs only choose $n = log(N)$, If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = N$ possible messages that Alice sent, and hopefully $N$ possible destinations.
+If we assume that there is not a Fort, then Alice needs only choose $n = log(N)$, If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = N$ possible messages that Alice sent, and hopefully $N$ possible destinations.
 The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose.
@@
 
-\subsection{The Palace} Assuming the set $S$ peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$.
-If $s = \phi*N$ peers are part of the palace, on average $E[P_{AB}] = 2^{-\phi log(N)}$.
-The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Palace members as peers.
+\subsection{The Fort} Assuming the set $S$ peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$.
+If $s = \phi*N$ peers are part of the fort, on average $E[P_{AB}] = 2^{-\phi log(N)}$.
+The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Fort members as peers.
 
@@
 
+\section{Conclusion}
+Conclusion words here about our network which is basically whatever we have in the introduction
+
 \newpage

### 2014-03-13 paper.tex
large edit

@@
-\documentclass[twocolumn]{paper}
+\documentclass[twocolumn,11pt,english]{paper}
 \usepackage{comment}
-\usepackage{authblk}
 \usepackage{tikz}
@@
 \usepackage{relsize}
+\usepackage[T1]{fontenc}
 \usepackage[margin=1.0in]{geometry}
@@
 \title{Blowship - Untraceable Instantaneous Message Transfer via a Central Server}
-\author[*]{John Carlyle}
-\author[**]{Morgan McDermott}
-\affil[*]{University of angry bees}
-\affil[**]{University of flightless dragons}
+\author{
+  Carlyle, John\\
+  \textit{jcarlyle@ucsc.edu}
+  \and
+  McDermott, Morgan\\
+  \textit{mmcdermo@ucsc.edu}
+}
 
@@
 
-In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized peer-to-peer (p2p) protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication.
-The primary reason behind a centeral server is to have a browser based service which needs a server to initialze the peer to peer network.
+In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized peer-to-peer (P2P) protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication.
+The primary reason behind a centeral server is to have a browser based service which needs a server to initialze the P2P network.
 
@@
 
-Traditional cryptography obsucres the message being sent from one party to another.
-This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: who the message is being sent to.
-Much work has been done to build networks that can obscure message passing by esentially mixing the messages around in a large group of peers in such a way that a peer in the network, or even a large group of peers cannot figure out where the message is going to end up.
-Many of these system rely upon the fact that the user is accessing a constantly avaible resource, such as with tor\cite{tor-design}, or in the case of email one can wait as long as nessesary for a message to be read by the user on the other end.
+Traditional cryptography hides the message being sent from one party to another.
+This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: to whom the message is sent.
+Much work has been done to build networks that can obscure message passing by esentially mixing the messages around in a large group of peers in such a way that a peer in the network, or even a large group of peers cannot figure out the message's final destination.
+Many of these systems rely upon the fact that the user is accessing a constantly avaible resource, such as with Tor\cite{tor-design}, or in the case of email one can wait as long as nessesary for a message to be read by the recipient.
 
-we are presenting to the reader is Untraceable Instantaneous Messaging, via a central server.
-Our system of message passing is initiated by the browser, allowing a person to browse to one central location and conveneintly use this service.
+We present to the reader Untraceable Instantaneous Messaging, via a central server.
+Our message passing system is initiated by the browser, allowing a person to browse to one central location and conveniently use this service.
+A much different experience than with using many other P2P communication protocols.
 The central server is primarily used as an entrypoint into a network of peers.
-The peers are used to obsfucate who is sending messages to whom, allowing the clients to communicate with both private content, all in as close to real time as possible given the constraints of the algorithms being used.
+The peers are used to obsfucate who is sending messages to whom, allowing the clients to communicate with both private content and correspondant, all in as close to real time as possible given the constraints of the algorithms being used.
 
@@
 \begin{description}
-\item[Mixes] Mixes are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies.
-Mixes have seen wide use since Chaum first introduced them in his 1981 paper \cite{chaum-mix}.
+\item[Mixes] are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies.
+Mixes have seen wide use since Chaum first introduced them in 1981 \cite{chaum-mix}.
 They have been used in systems such as MixMinion\cite{minion-design} to anonymously send and receive email.
-Onion routing systems such as Tor \cite{tor-design} use series of mixes as proxies for web data.
+Onion routing systems such as Tor \cite{tor-design} use a series of mixes as proxies for web data.
 
 \item[Nym systems] Pseudonymous message delivery systems enable users to send and receive messages with a \textit{nym} (pseudonym) that cannot be traced back to their true identity.
-Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient - which is what we are attempting to develop in this paper.
+Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient - which is what develop in this paper.
 
-\item[Private Information Retrieval] PIR has been used to facilitate anonymous communication in a variety of ways.
+\item[Private Information Retrieval] (PIR) has been used to facilitate anonymous communication in a variety of ways.
 The Pynchon Gate \cite{sassaman:wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees.
-Tor-PIR \cite{TODO} uses PIR to distribute information about servers without forcing users to download the entire directory.
+Tor-PIR \cite{MittalOTBG11} uses PIR to distribute information about servers without forcing users to download the entire directory.
 
@@
 \section{Measuring Anonymity}
-\textit{Anonymity sets}, introduced by Chaum in his Dining Cryptographers paper \cite{chaum-dc}, are widely used to analyze the anonymity provided by various p2p privacy schemes.
+Anonymity sets, introduced by \cite{chaum-dc}, are widely used to analyze the anonymity provided by various P2P privacy schemes.
 Given a message and whatever information an attacker has obtained, the anonymity set for that message is the set of users who could have sent it.
-An anonymity set of size 1 means that the attacker knows exactly who sent the message.
+For example, an anonymity set of size 1 means that the attacker knows exactly who sent the message.
 
@@
 To solve this problem, Diaz \cite{Diaz02} and Serjantov \cite{Serj02} independently developed almost identical solutions.
-Their idea is this: given a message, consider the probability distribution of its senders.
+Their solution is this: given a message, consider the probability distribution of its senders.
 The entropy of this probability distribution then represents the number of bits an attacker still needs to obtain in order to identify the sender of the message.
@@
 
-For example, if we give one user a probability $1$ of sending the message, all other users have probability 0, and $S = -(1 * 0) = 0$, meaning the attacker needs no more information to identify the user.
+Suppose we have a user such that his or her probability is $1$, then  $S = -(1 * 0) = 0$, meaning the attacker needs no more information to identify the user.
 
 \section{Privacy Goals}
-The goal of this system is to provide a method for communicating securely between parties through a central server with low latency and low communication overhead.
-We attempt to satisfy these requirements assuming the intermediate server may be compromised.
-By communicating securely we mean specifically (using terminology from \textbf{[6]}):
-\\\\\textbf{Communication Privacy}. Any party Eve cannot read the contents of intercepted messages sent between any two parties Alice and Bob. 
-\\\textbf{Participant Privacy}.
-This is also called \textbf{Unobservability} and \textbf{Untraceability}.
+The goal of this system is to provide a method for secure communication between parties through a central server with low latency and low communication overhead.
+We satisfy these requirements by assuming the intermediate server may be compromised.
+We define secuire communcation as thus \textbf{[6]}: FIX THIS CITE.
+Not sure which one it is.
+\\\\\textbf{Communication Privacy:} Any party Eve cannot read the contents of intercepted messages sent between any two parties, Alice and Bob. 
+\\\textbf{Participant Privacy:} This is also called \textbf{Unobservability} and \textbf{Untraceability}.
 Any party Eve cannot determine with probability $p > \epsilon$ that Alice and Bob are communicating, given any chosen $\epsilon$ (with a clear lower bound of $\epsilon > 1/N$ where $N$ is the number of participants).
 The ability of multiple participants to collude and determine this with $p > \epsilon$ must be well defined.
-\\\textbf{Destination Privacy}. Any party Eve in the network cannot determine the final destination of any party Alice's messages. This is a less stringent requirement than Participant Privacy.
+\\\textbf{Destination Privacy:} Any party Eve in the network cannot determine the final destination of any party Alice's messages. This is a less stringent requirement than Participant Privacy.
+
 \section{Central Server Communication}
-The majority of research into anonymous communication uses decentralized p2p networks.
+The majority of research into anonymous communication uses decentralized P2P networks.
 In some cases, however, it is necessary (and possibly beneficial) to communicate through a central server.
-Many of the developed p2p techniques can be adapted by using a pseudo-p2p protocol, by having peers communicate with each other indirectly through the central server.
+Many of the developed P2P techniques can be adapted by using a pseudo-P2P protocol, by having peers communicate with each other indirectly through the central server.
 
-In p2p protocols, delivering a message via a chain of peers or servers is a standard method to achieve anonymity.
+In P2P protocols, delivering a message via a chain of peers or servers is a standard method to achieve anonymity.
 In this system we'll use terminology from Tor and call the chain of peers a message passes through a $circuit$.
-A pseudo-p2p circuit then consists of an alternating chain of peer-server and server-peer communications.
+A pseudo-P2P circuit then consists of an alternating chain of peer-server and server-peer communications.
 
@@
       \draw [black] (37.2,-22.1) circle (3);
-\draw (37.2,-22.1) node {$S_2$};
+      \draw (37.2,-22.1) node {$S_1$};
       \draw [black] (44.5,-22.1) circle (3);
@@
   \end{center}
-  \caption{A simple pseudo-p2p circuit}
+  \caption{A simple pseudo-P2P circuit}
 \end{figure}
@@
 \item[The Fort] 
-  is Surge and penguins colluding. 
+  is Surge and Penguins colluding. 
 \end{description}
@@
 
-In this system, peers operate exactly as MIXes in the literature \cite{chaum-mix} .
-That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[soething]]], as well (as we will discuss) by reordering and batching messages.
+In this system, peers operate exactly as Mixes in the literature \cite{chaum-mix} .
+That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[something]]], as well (as we will discuss) by reordering and batching messages.
 \subsection{Security Flaws}
-Here we'll perform a simplified analysis of the security flaws of the basic, naive system described so far. 
+Here we'll perform a simplified analysis of the security flaws of the basic, na\"ive system described so far. 
 Let $P_{AB}$ be the probability that Alice sent a given message that was delivered to to Bob. 
 \begin{enumerate}
-\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $P_1 ...
-P_n$, $Surge$ can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$.
-This is because Surge knows that one of $A \cup \{P_1 ...
-P_n\}$ talked to Bob.
-\item\textbf{Collusion.} If  $s$ peers collude with Surge to form the Fort, then the Fort can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
-\item\textbf{Timing.} Even if $P_1 ...
-P_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking.
-\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases even more. 
+\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $p_1 \ldots p_n$ where $p_i$ is a penguin, Surge can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$.
+This is because Surge knows that one of $A \cup \{p_1 \ldots p_n\}$ talked to Bob.
+\item\textbf{Collusion.} If  $s$ peers collude with Surge to form The Fort, then The Fort can determine on average (depending on which peers Alice picked), that $P_{AB} > (n/(N-s)+1)^{-1}$ - that is, Alice has a chance $1 - (N-s)/N$ of each peer being compromised and not contributing to her privacy.
+\item\textbf{Timing.} Even if $p_1 ...
+p_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking.
+\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases exponentially. 
 \item\textbf{Man in the Middle.} If Alice acquries Bob's public key from Surge (and vice-versa), there's nothing to stop Surge from mounting a Man in the Middle attack given this simple model. 
@@
 \subsection{Solutions}
-To begin solving these problems, change the protocol so that any non-Penguin peer will always wait until it can send two or more messages simultaneously.
-This is equivilant to turning each peer into a 2-Threshold mix.
+To begin solving these problems, we will need to change the protocol so that any non-Penguin peer will always wait until it can send two or more messages simultaneously.
+This is equivilant to turning each peer into a 2-threshold mix.
 \cite{TODO}
 
-If we assume that there is not a Fort, then Alice needs only choose $n = log(N)$, If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = N$ possible messages that Alice sent, and hopefully $N$ possible destinations.
+If we assume that The Fort has not been established, then Alice only needs to choose $n = log(N)$, If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = N$ possible messages that Alice sent, and most likely $N$ possible destinations.
 The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose.
 If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$.
-Then, the $size$ of Alice's anonymity probability distribution is $\approx 1$ since the sender probabilities are roughly uniform.
+Then, the size of Alice's anonymity probability distribution is $\approx 1$ since the sender probabilities are roughly uniform.
 
 In this way Surge gains no information about the sender of the message.
-If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance $< n$ from Alice, and then $P_{AB} = 2^{-(log(N)-1)} = 2/N$, and $S = - \frac{1}{4} log(\frac{1}{2N})$ which is still reasonable, though Alice could compensate by randomly choosing the length of her circuit.
+If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance less than $n$ from Alice, and then $P_{AB} = 2^{-(log(N)-1)} = 2/N$, and $S = - \frac{1}{4} log(\frac{1}{2N})$ which is still reasonable, though Alice could compensate further by randomly choosing the length of her circuit.
 
-\subsection{The Fort} Assuming the set $S$ peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is unfortunately some chance that $R \subset S$ and so $P_{AB} = 1$.
-If $s = \phi*N$ peers are part of the fort, on average $E[P_{AB}] = 2^{-\phi log(N)}$.
-The chance Surge can tell with probability $> \gamma$ that Alice and Bob are talking to eachother, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Fort members as peers.
+\subsection{The Fort} Assuming the set $S$ peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is some chance that $R \subset S$ and so $P_{AB} = 1$.
+If $s = \phi*N$ peers are part of The Fort, on average $E[P_{AB}] = 2^{-\phi log(N)}$.
+The chance Surge can tell with probability greater than $\gamma$ that Alice and Bob are talking to each other, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Fort members as peers.
 
@@
 
-While less than ideal this is not bad. The chance that Surge, having $50\%$ of peers colluding with him, can tell that Alice is talking to Bob with probability $> 0.5$ is only $12\%$.
+While less than ideal, this is not unreasonable.
+The chance that Surge, having $50\%$ of peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is only $12\%$.
 
@@
 
-\subsection{Man in the Middle.} If both Alice and Bob are online, then they could use Diffie Hellman to ensure that Surge isn't acting as a Man in the middle.
+\subsection{Man in the Middle} If both Alice and Bob are online, then they could use Diffie-Hellman to ensure that Surge isn't acting as a Man in the Middle.
 However, we'd like to allow offline delivery of messages.
@@
 A mix holds on to incoming messages until its \textbf{flush function} is satisfied, then it forwards some subset of its collected messages.
-Common attacks are variants of the $n - 1$ or $flooding$ attack, in which an attacker fills the mix with its own fake messages and then sends the 1 message he wishes to track.
+Common attacks are variants of the $n - 1$, or $flooding$ attack, in which an attacker fills the mix with its own fake messages and then sends the 1 message he wishes to track.
 
@@
 A peer will at minimum send one dummy message along with every real message, maintaining a branching factor greater than two at every hop.
-Typically providing complete protection with cover traffic is difficult - it requires the mix to choose dummy message recipients uniformally from all users.
+Typically providing, complete protection with cover traffic is difficult - it requires the mix to choose dummy message recipients uniformally from all users.
 In our system, however, randomly and anonymously choosing other online peers is designed to be efficient.
@@
 \section{Applying PIR}
+\subsection{PIR usage}
 An obvious way to utilize PIR for anonymous communication is as a ``Dead Drop''.
-If we have a PIR server Charlie, Alice could write her messages to block $i$ in Charlie's PIR database, then bob could request block $i$ anonymously.
+If we have a PIR server Charlie, Alice could write her messages to block $i$ in Charlie's PIR database, then Bob could request block $i$ anonymously.
 This could enable us to increase the size of Alice's anonymity set (retaining a uniform distribution of probabilities, as well) while reducing our circuit length significantly.
 
-There are several problems with this configuration, however.
+\subsection{PIR issues}
+There are, however, several problems with this configuration.
 
-First, Alice must communicate Charlie's ID and $i$ to bob anonymously. This could happen via the pseudo-p2p protocol as above.
+First, Alice must communicate Charlie's ID and $i$ to Bob anonymously. This could happen via the pseudo-P2P protocol as above.
 
 Second, Alice and Bob both start talking to Charlie around the same time.
-If Charlie suspects Alice and Bob are talking to eachother, he can easily create a fake PIR database for all of Alice's inserts and all of Bob's retrievals, and if they continue to communicate normally he has found a connection.
+If Charlie suspects Alice and Bob are talking to each other, he can easily create a fake PIR database for all of Alice's inserts and all of Bob's retrievals, and if they continue to communicate normally he has discovered a connection.
 
@@
 \begin{description}
-\item[Pseudonymity.] Allow for parties to communicate securely without knowing eachother's identities.
-Currently our system relys heavily (at least when a person first enters the network) on the fact that the person initiating the communication knows the person's key with whom he wants to communciate.
+\item[Pseudonymity.] Allow for parties to communicate securely without knowing each other's identities.
+Currently our system relies heavily (at least when a person first enters the network) on the fact that the person initiating the communication knows the person's key with whom he wants to communciate.
 
@@
 \bibliography{paper.bib}
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 \end{document}

### 2014-03-13 paper.tex
Conventions:
Fleshy cleanup

@@
 Serjantov \cite{Serj02} calls this measure the \textit{size} $S$ of the anonymity probability distribution.
-Given $U$ is the set of all users, and $p_u$ is the probability that $u \in U$ sent the message under its probability distribution for users, then the $size$ of the probability distribution is:
+Given $U$, the set of all users, and $p_u$, the probability that $u \in U$ sent the message, then the $size$ of the probability distribution is:
 
@@
 We satisfy these requirements by assuming the intermediate server may be compromised.
-We define secuire communcation as thus \textbf{[6]}: FIX THIS CITE.
+We define secure communication as thus \textbf{[6]}: FIX THIS CITE.
 Not sure which one it is.
@@
 
-Alice can then send a message to bob that will follow the path $A \rightarrow P_1 \rightarrow S \rightarrow ... \rightarrow S \rightarrow P_n \rightarrow B$ by sending the following message to Surge: 
+Alice can then send a message to Bob that will follow the path $A \rightarrow P_1 \rightarrow S \rightarrow ... \rightarrow S \rightarrow P_n \rightarrow B$ by sending the following message to Surge: 
 \\
@@
 \begin{enumerate}
-\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $p_1 \ldots p_n$ where $p_i$ is a penguin, Surge can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$.
+\item\textbf{Linear Chain.} If we assume that Alice's message is the only message sent by any of $p_1 \ldots p_n$ where $p_i$ is a peer, Surge can determine that $P_{AB} > (n+1)^{-1} \gg 1/N$.
 This is because Surge knows that one of $A \cup \{p_1 \ldots p_n\}$ talked to Bob.
@@
 If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB} > 1/6$ chance that Alice is talking to Bob.
-If $60\%$ of peers are part of the Fort, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$.
+If $60\%$ of peers are part of the Fort, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$ which is very poor anonymity.
 
 \subsection{Solutions}
-To begin solving these problems, we will need to change the protocol so that any non-Penguin peer will always wait until it can send two or more messages simultaneously.
+To begin solving these problems, we will need to change the protocol so that any non-Penguin peer will always wait until it can send \textbf{two or more messages simultaneously}.
 This is equivilant to turning each peer into a 2-threshold mix.
@@
 
-If we assume that The Fort has not been established, then Alice only needs to choose $n = log(N)$, If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = N$ possible messages that Alice sent, and most likely $N$ possible destinations.
-The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose.
+If we assume that The Fort has not been established (no peers are colluding with Surge), then Alice only needs to choose $n = log(N)$ to remain anonymous from Surge.
+If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = 2^{log(n)} = N$ possible messages that Alice sent, and some $< N$ possible destinations.
+The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n = N$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose.
 If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$.
@@
 
-\subsection{The Fort} Assuming the set $S$ peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is some chance that $R \subset S$ and so $P_{AB} = 1$.
-If $s = \phi*N$ peers are part of The Fort, on average $E[P_{AB}] = 2^{-\phi log(N)}$.
+\subsection{The Fort} Assuming the set $S$ of peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is some chance that all chosen peers are colluding with Surge $(R \subset S)$ and so Alice's identity is completely compromised $(P_{AB} = 1$ and $S = 0)$.
+
+Let $\phi$ be the proportion of peers who are colluding with Surge.
+Then $s = \phi N$ peers are part of The Fort, and on average $(1 - \phi)n$ of $n$ chosen peers still help maintain privacy, leading to the expectation $E[P_{AB}] = 2^{-(1 - \phi) log(N)}$.
+
 The chance Surge can tell with probability greater than $\gamma$ that Alice and Bob are talking to each other, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Fort members as peers.
 
-This happens with probability $\sum\limits_{i=x}^n\phi^i$ where 
+Each peer has a probability $\phi$ of being part of the Fort, so Alice choosing $x$ or more colluding peers occurs with probability $\sum\limits_{i=x}^n\phi^i$ where 
 \\ $P_{AB} = 2^{-(n - x)} = 2^{-(log(N) - x)} = \gamma$
-\\ $x = 2^{loglog(N)/\gamma}$
+\\ $ \Rightarrow x = 2^{loglog(N)/\gamma}$
 
@@
 While less than ideal, this is not unreasonable.
-The chance that Surge, having $50\%$ of peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is only $12\%$.
+The chance that Surge, having $50\%$ of 1000 peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is only $12\%$.
 
@@
 A peer will at minimum send one dummy message along with every real message, maintaining a branching factor greater than two at every hop.
-Typically providing, complete protection with cover traffic is difficult - it requires the mix to choose dummy message recipients uniformally from all users.
+Typically, obtaining complete protection with cover traffic is difficult - it requires the mix to choose dummy message recipients uniformally from all users\cite{trickle02}.
 In our system, however, randomly and anonymously choosing other online peers is designed to be efficient.

### 2014-03-14 paper.tex
:THINGSGSGS

@@
-\documentclass[twocolumn,11pt,english]{paper}
+\documentclass[twocolumn,11pt,english]{article}
 \usepackage{comment}
@@
 \title{Blowship - Untraceable Instantaneous Message Transfer via a Central Server}
+\date{}
 \author{
@@
 This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: to whom the message is sent.
-Much work has been done to build networks that can obscure message passing by esentially mixing the messages around in a large group of peers in such a way that a peer in the network, or even a large group of peers cannot figure out the message's final destination.
+Much work has been done to build networks that can obscure message passing by esentially mixing the messages around in a large group of peers in such a way that a peer in the network, or even a large group of peers, cannot figure out the message's final destination.
 Many of these systems rely upon the fact that the user is accessing a constantly avaible resource, such as with Tor\cite{tor-design}, or in the case of email one can wait as long as nessesary for a message to be read by the recipient.
@@
 
-\section{Previous Work}
-\begin{description}
-\item[Mixes] are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies.
-Mixes have seen wide use since Chaum first introduced them in 1981 \cite{chaum-mix}.
-They have been used in systems such as MixMinion\cite{minion-design} to anonymously send and receive email.
-Onion routing systems such as Tor \cite{tor-design} use a series of mixes as proxies for web data.
+\section{Conventions}
+All logs in this paper are $\log_2$ unless otherwise specified.
+$N$ is the total number of peers in the network.
+A \textit{hop} is defined as a message passing from $peer_a$ to the server and then to $peer_b$, for reasons explained in section 5.
 
-\item[Nym systems] Pseudonymous message delivery systems enable users to send and receive messages with a \textit{nym} (pseudonym) that cannot be traced back to their true identity.
-Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient - which is what develop in this paper.
-
-\item[Private Information Retrieval] (PIR) has been used to facilitate anonymous communication in a variety of ways.
-The Pynchon Gate \cite{sassaman:wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees.
-Tor-PIR \cite{MittalOTBG11} uses PIR to distribute information about servers without forcing users to download the entire directory.
-
-\end{description}
-
-\section{Measuring Anonymity}
-Anonymity sets, introduced by \cite{chaum-dc}, are widely used to analyze the anonymity provided by various P2P privacy schemes.
+\subsection{Measuring Anonymity}
+Anonymity sets \cite{chaum-dc}, are widely used to analyze the anonymity provided by various P2P privacy schemes.
 Given a message and whatever information an attacker has obtained, the anonymity set for that message is the set of users who could have sent it.
@@
 \begin{center}
-  $ S = - \mathlarger{\sum}\limits_{u \in U} p_u $log$_2(p_u)$
+  $ S = - \mathlarger{\sum}\limits_{u \in U} p_u \log_2(p_u)$
 \end{center}
@@
 Suppose we have a user such that his or her probability is $1$, then  $S = -(1 * 0) = 0$, meaning the attacker needs no more information to identify the user.
+
+\subsection{Adversaries}
+In this context, we have several distinct types of adversaries we must consider:
+\begin{description}
+\item[Penguin] 
+  is any Peer who can intercept any messages and modify the content of that message.
+\item[Surge] 
+  is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
+\item[Proletariat] 
+  is a group of colluding Penguins.
+\item[The Fort] 
+  is Surge and a Proletariat colluding. In this situation Surge could be generating new peers to act as Penguins in order to form The Fort.
+\end{description}
+
+\section{Previous Work}
+The majority of research into anonymous communication uses decentralized P2P networks. In some cases, however, it is necessary (and possibly beneficial) to communicate through a central server.
+
+\subsection{Mixes}
+Mixes are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies.
+Mixes have seen wide use since Chaum first introduced them in 1981 \cite{chaum-mix}.
+They have been used in systems such as MixMinion\cite{minion-design} to anonymously send and receive email.
+Onion routing systems such as Tor \cite{tor-design} use a series of mixes as proxies for web data.
+
+\subsection{Nym systems} Pseudonymous message delivery systems enable users to send and receive messages with a \textit{nym} (pseudonym) that cannot be traced back to their true identity.
+Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient - which is what we develop in this paper.
+
+\subsection{Private Information Retrieval} Private Information Retrieval (PIR) has been used to facilitate anonymous communication in a variety of ways.
+The Pynchon Gate \cite{sassaman:wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees.
+Tor-PIR \cite{MittalOTBG11} uses PIR to distribute information about servers without forcing users to download the entire directory.
 
@@
 \\\textbf{Participant Privacy:} This is also called \textbf{Unobservability} and \textbf{Untraceability}.
-Any party Eve cannot determine with probability $p > \epsilon$ that Alice and Bob are communicating, given any chosen $\epsilon$ (with a clear lower bound of $\epsilon > 1/N$ where $N$ is the number of participants).
+Any party Eve cannot determine with probability $p > \epsilon$ that Alice and Bob are communicating, given any chosen $\epsilon$ with a clear lower bound of $\epsilon > 1/N$.
 The ability of multiple participants to collude and determine this with $p > \epsilon$ must be well defined.
@@
 
-\section{Central Server Communication}
-The majority of research into anonymous communication uses decentralized P2P networks.
-In some cases, however, it is necessary (and possibly beneficial) to communicate through a central server.
+\section{The Na\"ive Protocol}
 Many of the developed P2P techniques can be adapted by using a pseudo-P2P protocol, by having peers communicate with each other indirectly through the central server.
@@
 \end{figure}
-
-\subsection{Adversaries}
-In this context, we have several distinct types of adversaries we must consider:
-\begin{description}
-\item[Penguin] 
-  is any Peer who can intercept any messages and modify the content of that message.
-\item[Surge] 
-  is a compromised central Server. He can alter and intercept any messages passing through, and can provide bogus information to any peer.
-\item[Proletariat] 
-  is a group of colluding Penguins.
-\item[The Fort] 
-  is Surge and Penguins colluding. 
-\end{description}
 

### 2014-03-14 paper.tex
Changes

@@
 In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized peer-to-peer (P2P) protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication.
-The primary reason behind a centeral server is to have a browser based service which needs a server to initialze the P2P network.
+The primary reason behind a centeral server is to have a browser based service which needs a server to route for a pseudo-P2P network.
 
@@
 \item[Penguin] 
-  is any Peer who can intercept any messages and modify the content of that message.
+  is any malicious Peer. A penguin can send false messages to the server. 
 \item[Surge] 

### 2014-03-14 paper.tex
Thing

@@
 Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge.
+(This can be done using private information retrieval)
 
-Alice can then send a message to Bob that will follow the path $A \rightarrow P_1 \rightarrow S \rightarrow ... \rightarrow S \rightarrow P_n \rightarrow B$ by sending the following message to Surge: 
+Alice can then send a message to Bob that will follow the path $A \rightarrow P_1 \rightarrow S \rightarrow P_2 \rightarrow ...
+\rightarrow S \rightarrow P_n \rightarrow S \rightarrow B$ by sending the following message to Surge:
 \\
-Let $M = E_{KRA}[  time || nonce || message ]$
-\\Let $F_{ij}[x] = E_{KUi}[ ID_j || E_{KUj}[ x ] ]$
+Let \scriptsize$M = ID_A||E_{KRA}[ header || time || nonce || message ]$
+\normalsize
+\\Let \scriptsize$F_{ij}[x] = header||E_{KUi}[ ID_j || E_{KUj}[ x ] ]$
+\normalsize
 \\
@@
 
-If we assume that The Fort has not been established (no peers are colluding with Surge), then Alice only needs to choose $n = log(N)$ to remain anonymous from Surge.
-If every node sends 2 messages at once, and her message passes through $log(N)$ nodes, then there are $2^n = 2^{log(n)} = N$ possible messages that Alice sent, and some $< N$ possible destinations.
-The likelihood is that in $log(N)$ steps from Alice, there will be less than $2^n = N$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose.
-If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = log_z(N)$ and then $z^{log_z(N)} = 1/N$.
+If we assume that The Fort has not been established (no peers are colluding with Surge), then Alice only needs to choose $n = \log(N)$ to remain anonymous from Surge.
+If every node sends 2 messages at once, and her message passes through $\log(N)$ nodes, then there are $2^n = 2^{\log(n)} = N$ possible messages that Alice sent, and some $< N$ possible destinations.
+The likelihood is that in $\log(N)$ steps from Alice, there will be less than $2^n = N$ unique recipients of messages, but we can adjust for this by increasing the number of nodes $n$ we choose.
+If every node has an average unique branching factor of $z$ rather than $2$, we can just set $n = \log_z(N)$ and then $z^{\log_z(N)} = N$.
 Then, the size of Alice's anonymity probability distribution is $\approx 1$ since the sender probabilities are roughly uniform.
@@
 In this way Surge gains no information about the sender of the message.
-If Surge knows Alice will choose $n = log(N)$, then he can rule out any peer in the chain with distance less than $n$ from Alice, and then $P_{AB} = 2^{-(log(N)-1)} = 2/N$, and $S = - \frac{1}{4} log(\frac{1}{2N})$ which is still reasonable, though Alice could compensate further by randomly choosing the length of her circuit.
+If Surge knows Alice will choose $n = \log(N)$, then he can rule out any peer in the chain with distance less than $n$ from Alice, and then $P_{AB} = 2^{-(\log(N)-1)} = 2/N$, and $S = - \frac{1}{4} \log(\frac{1}{2N})$ which is still reasonable, though Alice could compensate further by randomly choosing the length of her circuit.
 
@@
 Let $\phi$ be the proportion of peers who are colluding with Surge.
-Then $s = \phi N$ peers are part of The Fort, and on average $(1 - \phi)n$ of $n$ chosen peers still help maintain privacy, leading to the expectation $E[P_{AB}] = 2^{-(1 - \phi) log(N)}$.
+Then $s = \phi N$ peers are part of The Fort, and on average $(1 - \phi)n$ of $n$ chosen peers still help maintain privacy, leading to the expectation $E[P_{AB}] = 2^{-(1 - \phi) \log(N)}$.
 
@@
 
-Each peer has a probability $\phi$ of being part of the Fort, so Alice choosing $x$ or more colluding peers occurs with probability $\sum\limits_{i=x}^n\phi^i$ where 
-\\ $P_{AB} = 2^{-(n - x)} = 2^{-(log(N) - x)} = \gamma$
-\\ $ \Rightarrow x = 2^{loglog(N)/\gamma}$
+Each peer has a probability $\phi$ of being part of the Fort, so Alice choosing $x$ or more colluding peers occurs with probability $\sum\limits_{i=x}^n\phi^ifdas$ where 
+\\ $P_{AB} = 2^{-(n - x)} = 2^{-(\log(N) - x)} = \gamma$
+\\ $ \Rightarrow x = 2^{\log\log(N)/\gamma}$
 

### 2014-03-15 paper.tex
LAMBERT

@@
 
-\subsection{Solutions}
+\section{Improved Protocol}
 To begin solving these problems, we will need to change the protocol so that any non-Penguin peer will always wait until it can send \textbf{two or more messages simultaneously}.
@@
 
-\subsection{The Fort} Assuming the set $S$ of peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is some chance that all chosen peers are colluding with Surge $(R \subset S)$ and so Alice's identity is completely compromised $(P_{AB} = 1$ and $S = 0)$.
+\subsection{Analysis of a simple message} 
+Using this improved pseudo-P2P message system, we will analyze the security of Alice sending a single message to Bob.
+
+Assuming the set $S$ of peers colludes with the server where $s = |S| > n$, and Alice chooses her circuit $C$ of peers randomly (where $|C| = n$), there is some chance that all chosen peers are colluding with Surge $(R \subset S)$ and so Alice's identity is completely compromised $(P_{AB} = 1$ and $S = 0)$.
 
@@
 The chance Surge can tell with probability greater than $\gamma$ that Alice and Bob are talking to each other, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Fort members as peers. 
+\begin{center}
+$\gamma = P_{AB} = 2^{-(n - x)} = 2^{-(\log(N) - x)}$
+\\ $ \Rightarrow x = log( \gamma ) + n$
+\end{center}
+Each peer has a probability $\phi$ of being part of the Fort, so Alice choosing $x$ or more colluding peers occurs with probability:
+\begin{center}
+ $p(P_{AB} > \gamma) = \mathlarger{\sum}\limits_{i=\log(\gamma) + n}^n {n \choose i} \phi^i (1 - \phi )^{n-i}$
 
-Each peer has a probability $\phi$ of being part of the Fort, so Alice choosing $x$ or more colluding peers occurs with probability $\sum\limits_{i=x}^n\phi^ifdas$ where 
-\\ $P_{AB} = 2^{-(n - x)} = 2^{-(\log(N) - x)} = \gamma$
-\\ $ \Rightarrow x = 2^{\log\log(N)/\gamma}$
+\end{center}
+
+Intuitively, Alice would be in an anonymity set of size 2 when $\gamma = 0.5$. This happens when all but one nodes are compromised: $x = log( 0.5 ) + n = n - 1$.
 
 \begin{figure}[ht]
+  \small
   \begin{tabular}{| l | l | l | l | l | l |}
+
     \hline
-    $\phi$ & N & $E[P_{AB}]$ & x & n & $p(P_{AB} > 0.5)$ \\\hline
-    0.5 & 1000 & 0.031 & 4 & 10 & 0.12\\
-    0.5 & 10000 & 0.01 & 4 & 14 & 0.12\\
-    0.5 & 100000 & 0.003 & 5 & 17 & 0.06\\
+    $\phi$ & N & n & x & $E[P_{AB}]$ & $p(P_{AB} > 0.5)$ \\\hline
+    0.8 & 1000 & 10 & 9 & 0.031 & 0.38\\
+    0.8 & 10000 & 14 & 13 & 0.010 & 0.20\\
+    0.8 & 100000 & 17 & 16 & 0.003 & 0.12\\
     \hline
@@
 
-While less than ideal, this is not unreasonable.
-The chance that Surge, having $50\%$ of 1000 peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is only $12\%$.
+\newpage
+As seen in table 42.42, the chance that Surge, having $80\%$ of 10000 peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is $20\%$.
+If Surge believes $P_{AB} = 0.5$ given 10000 peers, then the probability distribution size $S = 1.93$.
+
+If this level of security is unacceptable, the length of the circuit can be chosen based on an estimate of $\phi$ and an acceptable $p(P_{AB} > \gamma)$. Assuming $\gamma = 0.5$, then 
+\begin{center}
+$p(P_{AB} > 0.5)$ = $n\phi^{n-1} (1 - \phi ) + \phi^n $
+\end{center}
+
+Although n is difficult to solve for directly (requiring the Lambert W equation), a we give a graph for $n$ and $\phi$ given $\gamma = 0.5$:
+
+\includegraphics*[width=\linewidth]{gamma5graph.png}
+
+Given this graph it's clear that if the network is believed to be widely compromised, security can be made up for by choosing longer circuits.
+Although $\phi = 0.8$ makes $n = 10$ an unviable choice, at a circuit length of $n=20$ having $\phi = 0.8$ hardly affects the security.
 
@@
 \subsection{Peer Discovery and MITM brainstorming}
-
-Lying about who's online - If you want to send a message to a real node ``B'' but B is not listed as online, you won't send a message.
-However, if he lists ``B'' as online, ``B'' can be used to route messages validly by everyone.
 
@@
 \subsection{Peer Discovery}
-Unfortunately, if peers discover eachother through Surge, he can ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).
+Unfortunately, if peers discover eachother through Surge, he could ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).
 
@@
 Tor \cite{tor-design} likewise has a small number of trusted directory servers that share infrequently updated, signed directories.
+
+We solve this problem as follows:
 

### 2014-03-15 paper.tex
Figure
Meow

@@
 \subsection{Peer Discovery}
+Having a central server could make peer discovery much more efficient.
 Unfortunately, if peers discover eachother through Surge, he could ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).
@@
 
-We solve this problem as follows:
+We maintain the efficiency of a central directory server while
 

### 2014-03-15 paper.tex

@@
 \usepackage[margin=1.0in]{geometry}
+\usepackage{pstricks}
 
@@
 A \textit{hop} is defined as a message passing from $peer_a$ to the server and then to $peer_b$, for reasons explained in section 5.
+\begin{figure}[ht]
+  \begin{center}
+    \begin{tikzpicture}[scale=0.2]
+      \tikzstyle{every node}+=[inner sep=0pt]
+      \draw [black] (32.9,-14.9) circle (3);
+      \draw (32.9,-14.9) node {$S$};
+      \draw [black] (32.9,-14.9) circle (2.4);
+      \draw [black] (27.7,-24.3) circle (3);
+      \draw (27.7,-24.3) node {$P_1$};
+      \draw [black] (38.3,-24.3) circle (3);
+      \draw (38.3,-24.3) node {$P_2$};
+      \draw [black] (29.15,-21.67) -- (31.45,-17.53);
+      \fill [black] (31.45,-17.53) -- (30.62,-17.98) -- (31.5,-18.47);
+      \draw [black] (34.39,-17.5) -- (36.81,-21.7);
+      \fill [black] (36.81,-21.7) -- (36.84,-20.76) -- (35.97,-21.25);
+    \end{tikzpicture}
+  \end{center}
+\caption{A hop between two peers}
+\end{figure}
 
@@
 This is equivilant to turning each peer into a 2-threshold mix.
-\cite{TODO}
+\cite{trickle02}
 
@@
 
-\newpage
 As seen in table 42.42, the chance that Surge, having $80\%$ of 10000 peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is $20\%$.
@@
 
-\includegraphics*[width=\linewidth]{gamma5graph.png}
+\includegraphics*[width=\linewidth]{gamma5graph.eps}
 
@@
 \end{comment}
-
-\subsection{Peer Discovery and MITM brainstorming}
-
-Chain verification - Keep a web of trust with the length of the path to a person inversely proportional to how trusted they are.
-Share web of trust with those we communicate with - only share nodes with a certain level of trust, and then trust nodes discovered this way with diminished trust.
-
-If initial trust is only spread through person to person contact, then assigning negative trust is valuable because it reduces the value of colluding human nodes.
-
-* Have nodes sign messages as they pass through, so that the path can be tested/verified.
-
-\subsection{Peer Discovery}
-Having a central server could make peer discovery much more efficient.
-Unfortunately, if peers discover eachother through Surge, he could ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).
-
-This is a common problem in Onion routing schemes like Tor, as well as Mix networks.
-If directory servers collude with some routing servers, they can choose to only broadcast the existence of the compromised routing servers.
-
-MixMinion \cite{minion-design} solves these problems by having a small group of directory servers that only update nightly, having servers sign each other's directories, and ensuring that users download entire directories.
-These solutions are not feasible in our case since the set of online users is constantly in flux, and is likely to be too large to be sent to every user.
-Tor \cite{tor-design} likewise has a small number of trusted directory servers that share infrequently updated, signed directories.
-
-We maintain the efficiency of a central directory server while
-
-\subsection{Man in the Middle} If both Alice and Bob are online, then they could use Diffie-Hellman to ensure that Surge isn't acting as a Man in the Middle.
-However, we'd like to allow offline delivery of messages.
-
-This requires some form of web of trust, or some means of verifying public keys without trusting Surge.
-
-Users should maintain a list of known keys to make stuff good.
-
 \subsection{Peers as Mixes}
@@
 
-It would also be possible to use inter-mix detours\cite{TODO}, having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack.
+It would also be possible to use inter-mix detours\cite{trickle02}, having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack.
 However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system.
 
-\section{Applying PIR}
+\section{Peer Information Retrieval}
+Our system stores all information about which peers are online and their public keys in the central server.
+
+If Alice wishes to send a message to Bob, she needs to obtain the ID and public key for $n$ peers from the central server, as well as Bob's public key.
+To perform this request securely and efficiently, we use Private Information Retrieval (PIR).
+
+\subsection{Private Information Retrieval}
+  If Alice queried for information about these peers using a typical database, Surge would gain information about both who she is possibly talking to and which peers she uses in her circuits, dramatically reducing Alice's anonymity.
+
+However, using Private Information Retrieval, (first introduced by Chor and Goldreich \cite{pir}), it is possible to have Alice obtain this information without the server getting any information about the records she retrieved.
+
+The trivial way of achieving this is to send Alice the entire database.
+Although this is actually used in systems like Tor, it isn't practical given a system with thousands or possibly millions of records.
+
+The first Private Information Retrieval databases developed were  Information-Theoretical PIR (ITPIR), and operate by separating data between multiple servers.
+This model is fairly efficient, although it assumes the servers won't collude to discover user queries.
+
+With a single server, PIR was discovered to still be possible, however.
+Computational PIR (first introduced by Chor \cite{CPIR}) uses computationally difficult mechanisms to prevent a server hosting a single database from learning which records users retrieve from it.
+
+As a proof of concept, our system implements Gentry's CPIR system \cite{singledatabaseprivate}, which uses cyclic groups of prime powers to encode requests for data, and performs group operations to create a database response.
+This system has been analyzed and found to be less efficient than sending the entire database \cite{practicalPIR}(when considering a combination of both computation and communication overhead), but in the future we will implement a much faster lattice based system as analyzed by Olumofin and Goldberg in \cite{practicalPIR}.
+
+\subsection{Using PIR For Directories}
+To allow Alice to get information about which peers are online, their public keys, and the public keys of people she wishes to communicate with, we maintain two PIR databases.
+
+The first is a database of peers currently online, indexable by an integer between 0 and $N$, the number of online peers.
+Alice chooses peers for her circuits by querying for random indexes in this database:
+\\ \hfill\\ 
+\begin{tabular}{| l | l | l |}
+  \hline
+  Record ID & Peer ID & Peer Public Key \\ \hline
+  0 & 687542 & $pubkey_{687542}$  \\ \hline
+  1 & 552455 & $pubkey_{552455}$  \\ \hline
+  ... & ... & $...$  \\ \hline
+  n & 432314 & $pubkey_{432314}$  \\ \hline
+\end{tabular}
+
+\hfill\\\hfill\\The second is a similar database, except that it contains all known peers and is indexable by a user's ID. Alice uses this database to obtain Bob's public key:
+
+\hfill\\ 
+\begin{tabular}{| l | l | l |}
+  \hline
+  Peer ID & Peer Public Key \\ \hline
+  909787 & $pubkey_{909787}$  \\ \hline
+  424566 & $pubkey_{424566}$  \\ \hline
+  ... & $...$  \\ \hline
+  432314 & $pubkey_{432314}$  \\ \hline
+\end{tabular}
+
+\subsection{Peer Discovery}
+Using the model described above, peer discovery is efficient for users.
+Unfortunately, if peers discover eachother through Surge, he could ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).
+
+This is a common problem in Onion routing schemes like Tor, as well as Mix networks.
+If directory servers collude with some routing servers, they can choose to only broadcast the existence of the compromised routing servers.
+
+MixMinion \cite{minion-design} solves these problems by having a small group of directory servers that only update nightly, having servers sign each other's directories, and ensuring that users download entire directories.
+These solutions are not feasible in our case since the set of online users is constantly in flux, and is likely to be too large to be sent to every user.
+Tor \cite{tor-design} likewise has a small number of trusted directory servers that share infrequently updated, signed directories.
+
+In our system, however, a compromised Surge is disincentivized from lying about which peers are online.
+Consider a situation in which Alice wishes to send a message to Bob.
+If Surge doesn't report any non-colluding peers as online, then Alice won't send any messages to Bob since he appears to be offline.
+If Surge doesn't exclude non-colluding peers from the online list, however, Alice will inevitably include some of them in her chosen circuits.
+
+\subsection{Man in the Middle}
+
+In this model, it's trivial for Surge to mount a Man in the Middle attack.
+If Alice wishes to talk to Bob, she first obtains Bob's public key from Surge.
+If Surge lies about Bob's public key to everyone but Bob, he can intercept all messages sent to Bob, decrypt them with a fake private key he generated for Bob, and re-encrypt them with Bob's real public key.
+In this way no one realizes that all of Bob's messages are being intercepted.
+
+ Assuming that Surge can't lie about real peers being online (as discussed previously in Peer Discovery), Bob simply needs to ask random peers to query Surge for Bob's public key and send him the result.
+Requests sent to peers colluding with Surge could be faked, but Bob can send enough requests to gain any level of confidence he wishes that his key is being correctly distributed.
+
+If Surge is willing to allow Bob to learn that he's lying about public keys, Surge can share a fake public key with the world and masquerade as Bob, intercepting all initial messages sent to him and potentially learning the identities of Bob's associates.
+Worse, he could masquerade only when he knows Bob is offline, while lying and saying that Bob is actually online.
+
+The solution to this attack is twofold: users need to store the keys of friends and acquaintances they trust, and the protocol should ensure that initial communications don't include uniquely identifying information about the sender (perhaps using pseudonymous communication for the initial request).
+
+\subsection{Trust}
+
+Man in the Middle attacks can be further mitigated by maintaining a web of trust of public keys.
+To obtain an initial web of trust, we will use the PGP web of trust \cite{zimmermann1995official} in this system.
+Users may import their PGP keys and use them as their public keys on the system.
+This may tie user identities in the system to real identities, but this could be avoided by implementing pseudonymity in the system, and by allowing users to elect to use new keys.
+
+\section{Applying PIR to Routing}
 \subsection{PIR usage}
@@
 
+\section{Offline delivery of messages}
+ PYNCHON GATE
+
 \section{Future Work}
@@
 
-\item[Faster circuits.] Like Tor, we could use layers of symmetric encryption between successive pairs of peers in a circuit.
+\item[Faster encryption.] Like Tor, we could use layers of symmetric encryption between successive pairs of peers in a circuit.
 Using a public/symmetric system like Tor could help with pseudonymity as well.
@@
 This would allow us to require that the messages being sent are by computers that are also helping to suport the network.
+
+\item[Resilience.] Long circuits will inevitably lead to them breaking down due to people going offline intermittently. We need efficient ways of dealing with this.
+
+\item[Analyze performance of using PIR] a
+
+\item[Final summary/review of protocol]a
+
+\item[Final security analysis of protocol]a
+
+\item[User storage for data, keys, mail, etc]a
+
+\item[Analyze reusing people in circuits]a
+
+\item[Message Padding]a
+
+\item[Clarify why cover traffic is needed]a
 \end{description}
-
 \section{Conclusion}

### 2014-03-15 server/Client.py
Server client started

@@ -1,0 +1,111 @@
+from multiprocessing import Process, Manager
+import socket
+import threading
+import sys
+import ast
+
+lock = threading.RLock()
+
+def encrypt(data, key):
+    return data
+
+def generateCircuit(n, enduser, message, keys):
+    if enduser not in keys.keys():
+        return None
+
+    msg = enduser+"||"+encrypt("msg"+message, keys[enduser])
+    return msg    
+
+def user(name, p, msgs):
+    keys = {}
+    s = socket.socket()
+    host = socket.gethostname()
+    port = 8000
+    s.connect((host,port))
+    
+    if "init" == s.recv(1024):
+        print "connection started"
+        s.send("user"+name)
+
+    running = True
+    while running:
+
+        with lock:
+            for m in msgs:
+                print m
+            del msgs[:]
+        words = raw_input("Enter a command: ")
+        if words == ":bye" or words == ":logoff" or words == ":logout":
+            s.send(":bye")
+            running = False
+        if words == ":flush":
+            keys = {}
+            print "flushed keys"
+        if words == ":ks":
+            s.send(words)
+            keys_from_server = s.recv(1024)
+            print "Server: " + keys_from_server
+            keys = ast.literal_eval(keys_from_server)
+        if words == ":ls":
+            s.send(words)
+            print "Server: " + s.recv(1024)
+        if words.startswith(":send"):
+            words = words[6:]
+            index = words.find(" ")
+            target,msg = words[:index],words[index+1:]
+            
+            circuit = generateCircuit(5, target, name+": "+msg, keys)
+            if circuit == None:
+                print "Do not have that user's key, try :ks"
+            else:
+                s.send(circuit)
+        if words.startswith(":setkey"):
+            s.send(words)
+            print "Keys: %s" % s.recv(1024)
+
+    s.close()
+    p.terminate()
+
+
+def decrypt(data):
+    """
+    decrypt if you know what I mean wink wink nudge nudge
+    """
+    return data
+
+def circuit(name, msgs):
+    s = socket.socket()
+    host = socket.gethostname()
+    port = 8000
+    s.connect((host,port))
+
+    if "init" == s.recv(4):
+        s.send("circ"+name)
+        
+    running = True
+    while running:
+        d = s.recv(1024)
+        d = decrypt(d)
+        if "msg" == d[0:3]:
+            message = d[3:]
+            with lock:
+                msgs.append(message)
+        else:
[…]

### 2014-03-15 server/Server.py

@@ -1,0 +1,104 @@
+from multiprocessing import Process, Manager
+import socket
+import threading
+import time
+import sys
+
+lock = threading.RLock()
+
+def decrypt(data):
+    return data
+
+def process_client(c, ID_KEY, ID_STATUS, ID_SOCK):
+    c_id = c.recv(1024)
+    print c_id + " logged in"
+    with lock:
+        ID_STATUS[c_id] = True
+        ID_SOCK[c_id] = ""
+
+    running = True
+    while running:
+        v = c.recv(1024)
+        if v == ":bye":
+            print c_id + " logged out"
+            running = False
+            c.send("bye")
+        elif v.startswith(":setkey"):
+            v = v[7:]
+            v = v.strip()
+            with lock:
+                ID_KEY[c_id] = v
+            c.send("reset key to: " + v)
+            print c_id + " sent a new public key " + v
+        elif v.startswith(":ls"):
+            print "list requested, sending: %s" % ID_STATUS
+            c.send("%s" % filter(lambda x: ID_STATUS.get(x, False)  == True,ID_STATUS.keys()))
+        elif v.startswith(":ks"):
+            print "keys requested, sending: %s" % ID_KEY
+            c.send("%s" % ID_KEY)
+        else:
+            print "Got message: " + v
+            v = decrypt(v)
+            index = v.find("||")
+            forward,body = v[:index],v[index+2:]
+            print "sending " + body
+            with lock:
+                ID_SOCK[forward] = body
+
+
+    with lock:
+        ID_SOCK[c_id] = None
+        ID_STATUS[c_id] = False
+    c.close()
+
+
+def process_circuit(c, ID_KEY, ID_STATUS, ID_SOCK):
+    c_id = c.recv(1024)
+
+    running = True
+    while running:
+        time.sleep(1)
+        d = ID_SOCK[c_id] 
+        if d == None:
+            running = False
+        elif d != "":
+            c.send(d)
+            ID_SOCK[c_id] = ""
+
+    with lock:
+        del ID_SOCK[c_id]
+
+def process_data(c, ID_SOCK):
+    c_id = c.recv(4)
+    d = c.recv(1024)
+    ID_SOCK[c_id] = decrypt(d)
+    c.close()
+
+def main():
+    manager = Manager()
+    ID_KEY = manager.dict()
+    ID_STATUS = manager.dict()
+    ID_SOCK = manager.dict()
+
[…]

### 2014-03-16 server/Client.py
Hey they actually work now

@@ -1,3 +1,4 @@
+import rsa
 from multiprocessing import Process, Manager
 import socket
 import threading
@@ -5,31 +6,77 @@ import sys
 import ast
 
 lock = threading.RLock()
+hostname = socket.gethostname()
 
-def encrypt(data, key):
-    return data
+def readFromSocketUntil(s, signal="END"):
+    data_from_server = ""
+    block = ""
+    while block.find(signal) == -1:
+        block = str(s.recv(64))
+        data_from_server += block
+    data_from_server += block
+        
+    data_from_server = data_from_server[:data_from_server.find(signal)]
+    return data_from_server
+    
 
-def generateCircuit(n, enduser, message, keys):
+def encrypt(message, n, e, userId, svrkey):
+    """
+    Concatenate the userid with the current message and encrypt it with the keys
+    for userId
+    """
+    
+    def pad(s):
+        return "x" * (15 - len(s) % 15)
+
+    #encrypt and prepend the username
+    msg = rsa.encrypt(pad(message) + message, n, e, 15)
+    msg = userId + "||" + ":".join(map(str,msg))
+
+    #encrypt for server second, no name required since every other decryption goes through server anyway
+    msg = rsa.encrypt(pad(msg) + msg, svrkey[1], svrkey[0], 15)
+    msg = ":".join(map(str,msg))
+    return msg
+    
+def sendData(data):
+    tsock = socket.socket()
+    port = 8000
+    tsock.connect((hostname,port))
+    
+    if "init" == tsock.recv(4):
+        tsock.send("data"+data+"END")
+    tsock.close()
+
+def generateCircuit(n, enduser, message, keys, svrkeys):
     if enduser not in keys.keys():
         return None
 
-    msg = enduser+"||"+encrypt("msg"+message, keys[enduser])
-    return msg    
+    #first encrypt for the intended recipient
+    ct = encrypt(message, keys[enduser][1], keys[enduser][0], enduser, svrkeys)
+    return ct
 
-def user(name, p, msgs):
+
+def user(name, p, msgs, ned):
+    """
+    Presents user with a menu of options
+    Maintains a socket to the server to send requests for data.
+    Should open a new connection when sending a message for the first time
+    so that the server cannot tell the difference between a relay and 
+    the origin of a message
+    """
     keys = {}
     s = socket.socket()
-    host = socket.gethostname()
     port = 8000
     s.connect((host,port))
     
     if "init" == s.recv(1024):
         print "connection started"
         s.send("user"+name)
+        
[…]

### 2014-03-16 server/Server.py

@@ -1,3 +1,4 @@
+import rsa
 from multiprocessing import Process, Manager
 import socket
 import threading
@@ -6,15 +7,14 @@ import sys
 
 lock = threading.RLock()
 
-def decrypt(data):
-    return data
-
-def process_client(c, ID_KEY, ID_STATUS, ID_SOCK):
+def process_client(c, ID_KEY, ID_STATUS, ID_SOCK, ned):
     c_id = c.recv(1024)
     print c_id + " logged in"
     with lock:
         ID_STATUS[c_id] = True
         ID_SOCK[c_id] = ""
+
+    c.send(str(ned[1])+"n"+str(ned[0]))
 
     running = True
     while running:
@@ -25,7 +25,6 @@ def process_client(c, ID_KEY, ID_STATUS, ID_SOCK):
             c.send("bye")
         elif v.startswith(":setkey"):
             v = v[7:]
-            v = v.strip()
             with lock:
                 ID_KEY[c_id] = v
             c.send("reset key to: " + v)
@@ -35,15 +34,7 @@ def process_client(c, ID_KEY, ID_STATUS, ID_SOCK):
             c.send("%s" % filter(lambda x: ID_STATUS.get(x, False)  == True,ID_STATUS.keys()))
         elif v.startswith(":ks"):
             print "keys requested, sending: %s" % ID_KEY
-            c.send("%s" % ID_KEY)
-        else:
-            print "Got message: " + v
-            v = decrypt(v)
-            index = v.find("||")
-            forward,body = v[:index],v[index+2:]
-            print "sending " + body
-            with lock:
-                ID_SOCK[forward] = body
+            c.send("%sEND" % ID_KEY)
 
 
     with lock:
@@ -52,7 +43,7 @@ def process_client(c, ID_KEY, ID_STATUS, ID_SOCK):
     c.close()
 
 
-def process_circuit(c, ID_KEY, ID_STATUS, ID_SOCK):
+def process_circuit(c, ID_KEY, ID_STATUS, ID_SOCK, ned):
     c_id = c.recv(1024)
 
     running = True
@@ -62,19 +53,43 @@ def process_circuit(c, ID_KEY, ID_STATUS, ID_SOCK):
         if d == None:
             running = False
         elif d != "":
-            c.send(d)
+            c.send(d+"END")
             ID_SOCK[c_id] = ""
 
     with lock:
         del ID_SOCK[c_id]
 
-def process_data(c, ID_SOCK):
-    c_id = c.recv(4)
[…]

### 2014-03-16 server/rsa.py
Forgot rsa lib

@@ -1,0 +1,273 @@
+"""From https://gist.github.com/avalonalex/2122098"""
+
+import random
+from itertools import combinations
+import math
+import copy
+ 
+ 
+def euclid(a, b):
+    '''returns the Greatest Common Divisor of a and b'''
+    a = abs(a)
+    b = abs(b)
+    if a < b:
+        a, b = b, a
+    while b != 0:
+        a, b = b, a % b
+    return a
+ 
+ 
+def coprime(l):
+    '''returns 'True' if the values in the list L are all co-prime
+       otherwier, it returns 'False'. '''
+    for i, j in combinations(l, 2):
+        if euclid(i, j) != 1:
+            return False
+    return True
+ 
+ 
+def extendedEuclid(a, b):
+    '''return a tuple of three values: x, y and z, such that x is
+    the GCD of a and b, and x = y * a + z * b'''
+    if a == 0:
+        return (b, 0, 1)
+    else:
+        g, y, x = extendedEuclid(b % a, a)
+        return (g, x - (b // a) * y, y)
+ 
+ 
+def modInv(a, m):
+    '''returns the multiplicative inverse of a in modulo m as a
+       positve value between zero and m-1'''
+    # notice that a and m need to co-prime to each other.
+    if coprime([a, m]) == False:
+        return 0
+    else:
+        linearcombination = extendedEuclid(a, m)
+        return linearcombination[1] % m
+ 
+ 
+def extractTwos(m):
+    '''m is a positive integer. A tuple (s, d) of integers is returned
+    such that m = (2 ** s) * d.'''
+    # the problem can be break down to count how many '0's are there in
+    # the end of bin(m). This can be done this way: m & a stretch of '1's
+    # which can be represent as (2 ** n) - 1.
+    assert m >= 0
+    i = 0
+    while m & (2 ** i) == 0:
+        i += 1
+    return (i, m >> i)
+ 
+ 
+def int2baseTwo(x):
+    '''x is a positive integer. Convert it to base two as a list of integers
+    in reverse order as a list.'''
+    # repeating x >>= 1 and x & 1 will do the trick
+    assert x >= 0
+    bitInverse = []
+    while x != 0:
+        bitInverse.append(x & 1)
+        x >>= 1
+    return bitInverse
+ 
+ 
+def modExp(a, d, n):
+    '''returns a ** d (mod n)'''
+    assert d >= 0
+    assert n >= 0
+    base2D = int2baseTwo(d)
[…]

### 2014-03-16 server/Client.py
Fixed client hostname thing

@@ -6,7 +6,7 @@ import sys
 import ast
 
 lock = threading.RLock()
-hostname = socket.gethostname()
+host = socket.gethostname()
 
 def readFromSocketUntil(s, signal="END"):
     data_from_server = ""
@@ -41,7 +41,7 @@ def encrypt(message, n, e, userId, svrkey):
 def sendData(data):
     tsock = socket.socket()
     port = 8000
-    tsock.connect((hostname,port))
+    tsock.connect((host,port))
     
     if "init" == tsock.recv(4):
         tsock.send("data"+data+"END")
@@ -166,10 +166,11 @@ def circuit(name, msgs, ned):
 
 if __name__ == "__main__":
     name = sys.argv[1]
+    #this is dumb but doesn't seem worth it to use getopt
     try:
-        hostname = sys.argv[2]
+        host = sys.argv[2]
     except:
-        hostname = "localhost"
+        pass
     
     manager = Manager()
     msgs = manager.list()

### 2014-03-16 server/Client.py
Fxied two crashes

@@ -180,7 +180,7 @@ if __name__ == "__main__":
             ned = tuple(map(int,f.read().split("\n")[0:-1]))
             
     except IOError:
-        ned = (0,0,0)
+        ned = (1,1,1)
         print "No keys found, consider making some with :genkey"
 
     p = Process(target=circuit,args=(name,msgs,ned))

### 2014-03-16 server/Server.py

@@ -99,7 +99,7 @@ def main():
     s.setsockopt(socket.SOL_SOCKET, socket.SO_REUSEADDR, 1)
     hostname = socket.gethostname()
     port = 8000
-    s.bind((hostname,port))
+    s.bind(('',port))
     s.listen(5)
     
     while True:

### 2014-03-16 paper.tex
Makework good

@@
 \usepackage{pstricks}
+\usepackage{pgfplots}
 
-\title{Blowship - Untraceable Instantaneous Message Transfer via a Central Server}
+\title{Blowship - Untraceable Low-Latency Message Transfer via a Central Server}
 \date{}
@@
 Traditional cryptography hides the message being sent from one party to another.
-This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: to whom the message is sent.
-Much work has been done to build networks that can obscure message passing by esentially mixing the messages around in a large group of peers in such a way that a peer in the network, or even a large group of peers, cannot figure out the message's final destination.
-Many of these systems rely upon the fact that the user is accessing a constantly avaible resource, such as with Tor\cite{tor-design}, or in the case of email one can wait as long as nessesary for a message to be read by the recipient.
+This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: the connection between sender and recipient.
 
-We present to the reader Untraceable Instantaneous Messaging, via a central server.
-Our message passing system is initiated by the browser, allowing a person to browse to one central location and conveniently use this service.
-A much different experience than with using many other P2P communication protocols.
-The central server is primarily used as an entrypoint into a network of peers.
-The peers are used to obsfucate who is sending messages to whom, allowing the clients to communicate with both private content and correspondant, all in as close to real time as possible given the constraints of the algorithms being used.
+Much work has been done to build networks that can obscure this connection by passing the message through a series of peers in such a way that no peer, or even large group of peers, can determine its destination.
+Many of these systems route the message through dedicated peers that are always online (as with Mix systems \cite{chaum-mix}, like the popular Tor\cite{tor-design} anonymity system).
+Many of these systems are designed to relay email and as such have high latency (as in \cite{minion-design}, although there are systems like Tor designed specifically to have low latency.
+
+In most cases, these systems are highly decentralized.
+In Tor for example, the relay servers used are chosen by the client \cite{tor-design}, and the only ``central authority'' are the trusted directory servers.
+In this paper we explore building a highly centralized system, for use in cases where decentralization is difficult and to explore possible benefits.
+
+Current browsers have limited P2P communication capability - currently, they only have the ability to facilitate P2P distribution of media like video \cite{daoust2012towards}, and can't communicate with general purpose messages.
+For this reason, there are no pure P2P anonymization networks that operate at the browser level without using plugins.
+
+We present to the reader Untraceable Low-Latency Messaging via a Central Server.
+Our message system is accessed via the browser, allowing a person to browse to one central location and conveniently use this service, rather than using an external program for anonymity as with existing P2P services.
+The central server is acts as an intermediary and facilitator for the network of peers using it.
+The peers are used to obsfucate who is sending messages to whom, allowing the clients to maintain anonymity and message security, in as close to real time as possible.
+
+\section{Previous Work}
+The majority of research into anonymous communication uses decentralized P2P networks.
+In our work, we develop a centralized anonymous communication network using principles and protocols from these decentralized systems.
+
+\subsection{Mixes}
+Mixes are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies\cite{chaum-mix}.
+Mixes have seen wide use since Chaum first introduced them in 1981 \cite{chaum-mix}.
+In his protocol, mixes encrypt messages using public-private key cryptography so that incoming and outgoing messages have different content.
+For further security, messages have a fixed size, and mixes reorder messages before relaying them.
+
+ Mixes have been used in systems such as MixMinion\cite{minion-design} to anonymously send and receive email.
+Onion routing systems such as Tor \cite{tor-design} use a series of mixes as proxies for data.
+
+Some systems use a fixed route of Mixes (as in MixMinion), while others allow clients to choose their own route through the mixes (as in Tor).
+
+The anonymity mixes provide depends on many factors and was thoroughly analyzed by Serjantov in~\cite{trickle02}.
+In our system we use peers in the network as mixes, and will analyze their security using the known attacks that Serjantov presents (See Section~\ref{sec:PeersAsMixes} for a more in depth discussion).
+
+\subsection{Nym systems} Pseudonymous message delivery systems enable users to send and receive messages with a \textit{nym} (pseudonym) that cannot be traced back to their true identity \cite{sassaman:wpes2005}.
+Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient.
+Our paper implements exactly this forward channel, and so could easily be coupled with a Nym system.
+
+\subsection{Private Information Retrieval}
+
+Private Information Retrieval, first introduced by Chor and Goldreich \cite{pir}, allows a user to access information from a database without the database server learning the user's query.
+
+The trivial way of achieving this is to send the user the entire database.
+Although this is actually used in systems like Tor\cite{tor-design}, it may not be practical given a database with thousands or possibly millions of records.
+
+The first Private Information Retrieval databases developed were  Information-Theoretical PIR (ITPIR), and operate by separating data between multiple servers\cite{pir}.
+This model is fairly efficient, although it assumes the servers won't collude to discover user queries.
+
+With a single server, PIR was discovered to still be possible, however.
+Computational PIR (first introduced by Chor \cite{CPIR}) uses computationally difficult mechanisms to prevent a server hosting a single database from learning which records users retrieve from it.
+
+In all known PIR systems, query anonymity comes at a cost.
+It has been shown that the database must perform an $O(n)$ operation to respond to each query\cite{CPIR}, where $n$ is the size of the database.
+If this weren't the case, the database wouldn't touch every bit in the database to respond to a query and would gain some information about the query itself.
+
+Additionally, there is communication overhead in all known PIR systems. Responses to queries are usually polynomial or polylogarithmic in $n$ \cite{CPIR} \cite{pir}.
+
+Private Information Retrieval has been used to facilitate anonymous communication in a variety of ways.
+The Pynchon Gate \cite{sassaman:wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees.
+Tor-PIR \cite{MittalOTBG11} uses PIR to distribute information about servers without forcing users to download the entire directory.
+In our paper, we use PIR for directory services and investigate the possibility of using it for anonymous communication.
 
@@
 \item[The Fort] 
-  is Surge and a Proletariat colluding. In this situation Surge could be generating new peers to act as Penguins in order to form The Fort.
+  is Surge and a Proletariat colluding. Surge could also form the Fort by generating artificial peers to act as Penguins.
 \end{description}
-
-\section{Previous Work}
-The majority of research into anonymous communication uses decentralized P2P networks. In some cases, however, it is necessary (and possibly beneficial) to communicate through a central server.
-
-\subsection{Mixes}
-Mixes are servers through which encrypted messages are sent, hiding the correlation between incoming and outgoing messages using encryption, pooling incoming messages, and a variety of other strategies.
-Mixes have seen wide use since Chaum first introduced them in 1981 \cite{chaum-mix}.
-They have been used in systems such as MixMinion\cite{minion-design} to anonymously send and receive email.
-Onion routing systems such as Tor \cite{tor-design} use a series of mixes as proxies for web data.
-
-\subsection{Nym systems} Pseudonymous message delivery systems enable users to send and receive messages with a \textit{nym} (pseudonym) that cannot be traced back to their true identity.
-Many of these systems rely on having an anonymous ``forward'' channel that allows a user to send a message without attackers being able to deduce the recipient - which is what we develop in this paper.
-
-\subsection{Private Information Retrieval} Private Information Retrieval (PIR) has been used to facilitate anonymous communication in a variety of ways.
-The Pynchon Gate \cite{sassaman:wpes2005} is a nym system that uses information-theoretic PIR as a layer of indirection between a user and their nym - allowing users to retrieve mail sent to their nym with information-theoretic privacy guarantees.
-Tor-PIR \cite{MittalOTBG11} uses PIR to distribute information about servers without forcing users to download the entire directory.
 
@@
 We satisfy these requirements by assuming the intermediate server may be compromised.
-We define secure communication as thus \textbf{[6]}: FIX THIS CITE.
-Not sure which one it is.
-\\\\\textbf{Communication Privacy:} Any party Eve cannot read the contents of intercepted messages sent between any two parties, Alice and Bob. 
-\\\textbf{Participant Privacy:} This is also called \textbf{Unobservability} and \textbf{Untraceability}.
-Any party Eve cannot determine with probability $p > \epsilon$ that Alice and Bob are communicating, given any chosen $\epsilon$ with a clear lower bound of $\epsilon > 1/N$.
+We define secure communication as:
+\begin{enumerate}
+\item\textbf{Communication Privacy:} Any party Eve cannot read the contents of intercepted messages sent between any two parties, Alice and Bob. 
+\item\textbf{Untraceability:} This is also called \textbf{Unobservability}.
+Our definition is that any party Eve cannot determine with probability $p > \epsilon$ that Alice and Bob are communicating, given a chosen $\epsilon$ (with a clear lower bound of $\epsilon > 1/N$).
 The ability of multiple participants to collude and determine this with $p > \epsilon$ must be well defined.
-\\\textbf{Destination Privacy:} Any party Eve in the network cannot determine the final destination of any party Alice's messages. This is a less stringent requirement than Participant Privacy.
-
+\end{enumerate}
 \section{The Na\"ive Protocol}
-Many of the developed P2P techniques can be adapted by using a pseudo-P2P protocol, by having peers communicate with each other indirectly through the central server.
+Many of the developed P2P techniques can be adapted by using a pseudo-P2P protocol, having peers communicate with each other indirectly through the central server.
 
 In P2P protocols, delivering a message via a chain of peers or servers is a standard method to achieve anonymity.
-In this system we'll use terminology from Tor and call the chain of peers a message passes through a $circuit$.
+In this system we'll use terminology from Tor\cite{tor-design} and call the chain of peers a message passes through a $circuit$.
 A pseudo-P2P circuit then consists of an alternating chain of peer-server and server-peer communications.
@@
 Assume that Alice has obtained Bob's public key and unique ID while maintaining her anonymity.
-This could be done using a public keyserver of some kind, or perhaps they have exchanged keys in advance through some other channel.
-Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge.
-(This can be done using private information retrieval)
+This could be achieved using our directory service as outlined in Section~\ref{sec:PIRDirectories}, or by exchanging keys in advance through some other channel.
+Assume also that Alice can obtain the public keys and IDs for $n \le N$ peers at random while hiding her choice from Surge (This again can be done using the service in Section~\ref{sec:PIRDirectories}).
 
-Alice can then send a message to Bob that will follow the path $A \rightarrow P_1 \rightarrow S \rightarrow P_2 \rightarrow ...
-\rightarrow S \rightarrow P_n \rightarrow S \rightarrow B$ by sending the following message to Surge:
+Alice can then send a message to Bob that will follow the path 
+\\$A \rightarrow P_1 \rightarrow S \rightarrow P_2 \rightarrow ... \rightarrow S \rightarrow P_n \rightarrow S \rightarrow B$ 
+She sends this message by wrapping the initial data in successive layers of message headers and encryption as in Figure~\ref{messageStructure}.
 \\
+\begin{figure}[h]
 Let \scriptsize$M = ID_A||E_{KRA}[ header || time || nonce || message ]$
@@
 \\
-Alice sends: $F_{S1}[F_{S2}[...F_{nB}[ M ]]]$ to Surge.
+Final Message: $F_{S1}[F_{S2}[...F_{SB}[ M ]]]$
+\caption{Message Structure}
+\label{messageStructure}
+\end{figure}
 
@@
 In this system, peers operate exactly as Mixes in the literature \cite{chaum-mix} .
-That is, they prevent traffic correlation by removing a layer of encryption, prevent relay attacks [[[something]]], as well (as we will discuss) by reordering and batching messages.
+That is, they prevent traffic correlation by removing a layer of encryption, as well (as we will discuss) by reordering and batching messages.
+
+This system is designed so that without collusion from Surge, Penguins or a Proletariat are powerless to do anything but to delay or fail to forward messages.
+They don't know the ID of the next person they are forwarding the message to (since it's encrypted with the server's key), and obtain no other information when forwarding messages.
 \subsection{Security Flaws}
@@
 p_n$ are sending other messages, if Surge knows the probability distribution of the peer delay between receiving a message and forwarding it, he can discover the increased probability that Alice and Bob are talking.
-\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases exponentially. 
+\item\textbf{Multiple Communications.} If Alice sends another message to Bob, or Bob back to Alice, the chance that they are communicating increases dramatically. 
 \item\textbf{Man in the Middle.} If Alice acquries Bob's public key from Surge (and vice-versa), there's nothing to stop Surge from mounting a Man in the Middle attack given this simple model. 
@@
 This is fairly poor security.
-If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB} > 1/6$ chance that Alice is talking to Bob.
-If $60\%$ of peers are part of the Fort, then Surge possibly knows $P_{AB} = 1$ if $n \subset s$, but the expectation is $E[P_{AB}] = 1/3$ which is very poor anonymity.
+If Alice chooses $n = 5$, then if her chosen peers send no other messages until hers is delivered, Surge knows $P_{AB}$, the probability that Alice is talking to Bob, is $> 1/6$.
+If $60\%$ of peers are part of the Fort, then Surge possibly knows $P_{AB} = 1$ (if $n \subset s$), but the expectation is $E[P_{AB}] = 1/3$ which is very poor anonymity.
 
@@
 
-\subsection{Analysis of a simple message} 
-Using this improved pseudo-P2P message system, we will analyze the security of Alice sending a single message to Bob.
+\subsection{Peers as Mixes}
+\label{sec:PeersAsMixes}
+As previously discussed, peers act as mixes in this system - inheriting both their benefits and vulnerabilities.
+Many types of mixes have been developed, and Serjantov \cite{trickle02} has compiled common attacks and solutions.
+A mix holds on to incoming messages until its \textbf{flush function} is satisfied, then it forwards some subset of its collected messages.
+Common attacks are variants of the $n - 1$, or $flooding$ attack, in which an attacker fills the mix with its own fake messages and then sends the 1 message he wishes to track.
+
+All known mix types are vulnerable to such exact attacks \cite{trickle02} -  attacks that allow an attacker to know whether his attack was successful or not and try again if not.
+Since in our threat model Surge has complete access to the message history of each peer as well as the ability to delay and insert as many messages as he desires, trying to prevent these attacks by implementing a better flush function is even more futile.
+
+In our case, Surge can bypass the benefits obtained from turning peers into 2-Threshhold mixes by delivering one of his own false message-forward-requests along with every real message sent to each peer, so he can disregard one branch and essentially remove the anonymity gained from each hop in the circuit.
+
+Fortunately, due to the nature of this system we can provide almost complete protection with \textbf{cover traffic} \cite{trickle02}, or having each peer send dummy messages along with the messages it's forwarding.
+A peer will at minimum send one dummy message along with every real message, maintaining a branching factor greater than two at every hop.
+Typically, obtaining complete protection with cover traffic is difficult - it requires the mix to choose dummy message recipients uniformally from all users\cite{trickle02}.
+In our system, however, randomly and anonymously choosing other online peers is designed to be efficient.
+
+It would also be possible to use inter-mix detours\cite{trickle02}, having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack.
+However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system.
+
+\subsection{Anonymity inside The Fort} 
+Using this improved pseudo-P2P message system, we will analyze the security of Alice sending a single message to Bob when Surge colludes with Penguins to form The Fort.
 
@@
 
-The chance Surge can tell with probability greater than $\gamma$ that Alice and Bob are talking to each other, $p(P_{AB} > \gamma)$ requires Alice choosing $x$ Fort members as peers. 
+The chance Surge can tell with probability greater than $\gamma$ that Alice and Bob are talking to each other, $p(P_{AB} > \gamma)$, gives reasonable intuition into the \textit{worst-case} security of the system considering passing messages through circuits of peers.
+It can be interpreted as the probability that Alice has been ``found out'' to some specified degree.
+
+If we assume that Alice is the ``prime suspect'', and that all other peers have a uniform distribution of probability assigned to them, we get that $S$ (the number of bits the attacker still needs to gain) is:
+
+\begin{center}
+$-S = (1 - \gamma) \log(\frac{1-\gamma}{N - 1}) + \gamma \log(\gamma)$
+\end{center}
+
+To gain an intuition about what values of $\gamma$ mean, we can then plot $S$ for various values of $\gamma$
+\begin{figure}[h!]
+  \begin{tikzpicture}[scale=0.8]
+    \begin{axis}[
+      xlabel=$\gamma$
+      ,ylabel = $(1-\phi)N$
+      ,zlabel = $S$
+      ,z label style = {rotate=270}
+      ,ztick = {0,5,...,25}
+      ,ytick = {100, 1000, 10000, 100000}
+      ,ymode = log
+      ,log basis y={10}
+      ]
+      \addplot3[surf, mesh/interior colormap={blueblack}{color=(orange) color=(white)},
+      colormap/blackwhite, domain=0:1, y domain =100:100000, range = 0:20] { -1 * (((1 - x) * log2((1 - x)/(y-1)) + x * log2(x) )) };
+    \end{axis}
+  \end{tikzpicture}  
+  \caption{Relating $\gamma$ and $S$}
+  \label{gammaS}
+\end{figure}
+
+As we can see in Figure~\ref{gammaS}, having additional peers in the network (higher $N$ values) only helps increase Alice's anonymity ($S$ value) when $\gamma$ is small.
+That is, having more peers in the network doesn't really mitigate the security lost if Surge already believes that Alice sent a message with probability $0 \ll \gamma < 1 $.
+
+\subsection{Likelihood of the worst-case}
+We'd like to know how likely the worst-case ($p(P_{AB} > \gamma)$) scenario is given the circuit length chosen by Alice.
+
+If we let $x$ be the number of compromised peers Alice must choose such that $p(P_{AB} > \gamma)$, we obtain: 
 \begin{center}
@@
 
-Intuitively, Alice would be in an anonymity set of size 2 when $\gamma = 0.5$. This happens when all but one nodes are compromised: $x = log( 0.5 ) + n = n - 1$.
+Intuitively, Alice would be in an anonymity set of size 2 when $\gamma = 0.5$. This happens when all but one nodes are compromised, as indicated by our derived value $x = log( 0.5 ) + n = n - 1$.
 
-\begin{figure}[ht]
+\begin{figure}[h]
   \small
@@
   \end{tabular}
-  \caption{Table 42.42 - Probabilities things are bad}
+  \caption{Probability of the worst-case}
+  \label{WorstCaseTable}
 \end{figure}
 
-As seen in table 42.42, the chance that Surge, having $80\%$ of 10000 peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is $20\%$.
-If Surge believes $P_{AB} = 0.5$ given 10000 peers, then the probability distribution size $S = 1.93$.
+As seen in Table~\ref{WorstCaseTable} , the chance that Surge, having $80\%$ of 10000 peers colluding with him, can tell that Alice is talking to Bob with probability greater than $0.5$ is $20\%$.
+For reference, if Surge believes $P_{AB} = 0.5$ given the 2000 uncompromised peers, then the probability distribution size $S = 1.93$.
 
+\subsection{Longer Circuits}
 If this level of security is unacceptable, the length of the circuit can be chosen based on an estimate of $\phi$ and an acceptable $p(P_{AB} > \gamma)$. Assuming $\gamma = 0.5$, then 
@@
 
+\begin{figure}[h]
 \includegraphics*[width=\linewidth]{gamma5graph.eps}
+\caption{$p(P_{AB} > 0.5)$ given $n$ and $\phi$}
+\label{gamma5graph}
+\end{figure}
 
-Given this graph it's clear that if the network is believed to be widely compromised, security can be made up for by choosing longer circuits.
-Although $\phi = 0.8$ makes $n = 10$ an unviable choice, at a circuit length of $n=20$ having $\phi = 0.8$ hardly affects the security.
+Given Figure~\ref{gamma5graph} it's clear that if the network is believed to be widely compromised, security can be made up for by choosing longer circuits.
+Although $\phi = 0.8$ makes $n = 10$ an unviable choice, at a circuit length of $n=20$ having $\phi = 0.8$ barely increases the likelihood of the worst-case.
 
@@
 \end{comment}
-\subsection{Peers as Mixes}
-As previously discussed, peers act as mixes in this system - inheriting both their benefits and vulnerabilities.
-Many types of mixes have been developed, and Serjantov \cite{trickle02} has compiled common attacks and solutions.
-A mix holds on to incoming messages until its \textbf{flush function} is satisfied, then it forwards some subset of its collected messages.
-Common attacks are variants of the $n - 1$, or $flooding$ attack, in which an attacker fills the mix with its own fake messages and then sends the 1 message he wishes to track.
-
-All known mix types are vulnerable to such exact attacks \cite{trickle02} -  attacks that allow an attacker to know whether his attack was successful or not and try again if not.
-Since in our threat model Surge has complete access to the message history of each peer as well as the ability to delay and insert as many messages as he desires, trying to prevent these attacks by implementing a better flush function is even more futile.
-
-Fortunately, due to the nature of this system we can provide almost complete protection with \textbf{cover traffic} \cite{trickle02}, or having each peer send dummy messages along with the messages it's forwarding.
-A peer will at minimum send one dummy message along with every real message, maintaining a branching factor greater than two at every hop.
-Typically, obtaining complete protection with cover traffic is difficult - it requires the mix to choose dummy message recipients uniformally from all users\cite{trickle02}.
-In our system, however, randomly and anonymously choosing other online peers is designed to be efficient.
-
-It would also be possible to use inter-mix detours\cite{trickle02}, having peers randomly decide to introduce new hops to prevent Surge from recognizing his own messages sent during an $n - 1$ attack.
-However, this reduces reliability, increases latency, and given the protection that cover traffic provides seems unnecessary in this system.
 
@@
 
-However, using Private Information Retrieval, (first introduced by Chor and Goldreich \cite{pir}), it is possible to have Alice obtain this information without the server getting any information about the records she retrieved.
-
-The trivial way of achieving this is to send Alice the entire database.
-Although this is actually used in systems like Tor, it isn't practical given a system with thousands or possibly millions of records.
-
-The first Private Information Retrieval databases developed were  Information-Theoretical PIR (ITPIR), and operate by separating data between multiple servers.
-This model is fairly efficient, although it assumes the servers won't collude to discover user queries.
-
-With a single server, PIR was discovered to still be possible, however.
-Computational PIR (first introduced by Chor \cite{CPIR}) uses computationally difficult mechanisms to prevent a server hosting a single database from learning which records users retrieve from it.
+However, using Private Information Retrieval, it is possible to have Alice obtain this information without the server getting any information about the records she retrieved.
 
@@
 \subsection{Using PIR For Directories}
+\label{sec:PIRDirectories}
 To allow Alice to get information about which peers are online, their public keys, and the public keys of people she wishes to communicate with, we maintain two PIR databases.
 
-The first is a database of peers currently online, indexable by an integer between 0 and $N$, the number of online peers.
-Alice chooses peers for her circuits by querying for random indexes in this database:
-\\ \hfill\\ 
+The first is a database of peers currently online (Figure~\ref{onlinePeerDB}), indexable by an integer between 0 and $N$, the number of online peers.
+To reduce the number of PIR requests, we redundantly include the public keys in this database.
+Alice chooses peers for her circuits by querying using random indexes in this database:
+
+\begin{figure}[ht]
+  \centering
 \begin{tabular}{| l | l | l |}
@@
   ... & ... & $...$  \\ \hline
-  n & 432314 & $pubkey_{432314}$  \\ \hline
+  $N$ & 432314 & $pubkey_{432314}$  \\ \hline
 \end{tabular}
+\caption{The Online-Peer Database}
+\label{onlinePeerDB}
+\end{figure}
 
-\hfill\\\hfill\\The second is a similar database, except that it contains all known peers and is indexable by a user's ID. Alice uses this database to obtain Bob's public key:
+The second is a similar database (Figure~\ref{peerKeyDB}), that contains all known peers (online and offline) and is indexable by a user's ID.
+Alice uses this database to lookup the public keys of message recipients by their peer ID (which she can't do in the first database).
 
-\hfill\\ 
-\begin{tabular}{| l | l | l |}
+\begin{figure}[ht]
+  \centering
+\begin{tabular}{| l | l | }
   \hline
@@
   424566 & $pubkey_{424566}$ \\ \hline
-  ... & $...$  \\ \hline
+  ... & ... \\ \hline
   432314 & $pubkey_{432314}$  \\ \hline
 \end{tabular}
+\caption{The Peer Key Database}
+\label{peerKeyDB}
+\end{figure}
 
 \subsection{Peer Discovery}
-Using the model described above, peer discovery is efficient for users.
+\label{sec:PeerDiscovery}
+Using the model described above, choosing random peers for use in a circuit is efficient for users.
 Unfortunately, if peers discover eachother through Surge, he could ensure that any peer only knows about compromised peers (Effectively making $\phi = 1$).
@@
 If Surge doesn't exclude non-colluding peers from the online list, however, Alice will inevitably include some of them in her chosen circuits.
+Since Surge doesn't know that Alice and Bob are communicating beforehand, he is forced to either include or exclude all non-colluding peers from the online-peers database as a whole.
 
@@
 
- Assuming that Surge can't lie about real peers being online (as discussed previously in Peer Discovery), Bob simply needs to ask random peers to query Surge for Bob's public key and send him the result.
+ Assuming that Surge can't lie about real peers being online (as discussed in Section~\ref{sec:PeerDiscovery}), Bob simply needs to ask random peers to query Surge for Bob's public key and send him the result (We will call this \textbf{Auditing}).
 Requests sent to peers colluding with Surge could be faked, but Bob can send enough requests to gain any level of confidence he wishes that his key is being correctly distributed.

### 2014-03-16 server/Client.py
Pickle instead of my terrible thing

@@ -1,3 +1,4 @@
+import pickle
 import rsa
 from multiprocessing import Process, Manager
 import socket
@@ -31,11 +32,13 @@ def encrypt(message, n, e, userId, svrkey):
 
     #encrypt and prepend the username
     msg = rsa.encrypt(pad(message) + message, n, e, 15)
-    msg = userId + "||" + ":".join(map(str,msg))
+    msg = userId + "||" + pickle.dumps(msg,2)
+
 
     #encrypt for server second, no name required since every other decryption goes through server anyway
     msg = rsa.encrypt(pad(msg) + msg, svrkey[1], svrkey[0], 15)
-    msg = ":".join(map(str,msg))
+    msg = pickle.dumps(msg,2)
+
     return msg
     
 def sendData(data):
@@ -133,7 +136,8 @@ def decrypt(data,ned):
     """
     decrypt if you know what I mean wink wink nudge nudge
     """
-    data = map(int,data.split(":"))
+    data = pickle.loads(data)
+#    data = map(int,data.split(":"))
     return rsa.decrypt(data, ned[0], ned[2], 15)
 
 

### 2014-03-16 server/Server.py

@@ -1,3 +1,4 @@
+import pickle
 import rsa
 from multiprocessing import Process, Manager
 import socket
@@ -66,24 +67,24 @@ def process_data(c, ID_SOCK, ned):
     Put the encrypted portion of the message into the SOCK dictionary
     for that user
     """
-
-    #read data until END
-    d = ""
-    block = ""
-    while block.find("END") == -1:
-        block = str(c.recv(64))
+    with lock:
+        #read data until END
+        d = ""
+        block = ""
+        while block.find("END") == -1:
+            block = str(c.recv(64))
+            d += block
         d += block
-    d += block
-    d = d[:d.find("END")]
+        d = d[:d.find("END")]
 
-    #reformat to integer list
-    d = map(int, d.split(":"))
-    d = rsa.decrypt(d, ned[0], ned[2], 15)
-    d = d.split("||")
+        #reformat to integer list
+        d = pickle.loads(d)
+        d = rsa.decrypt(d, ned[0], ned[2], 15)
+        d = d.split("||")
     
-    name = d[0].lstrip("x")
-    #write result to socket for another user to await transfer
-    ID_SOCK[name] = d[1] 
+        name = d[0].lstrip("x")
+        #write result to socket for another user to await transfer
+        ID_SOCK[name] = d[1] 
     c.close()
 
 def main():
@@ -111,6 +112,7 @@ def main():
         elif "circ" == v:
             Process(target=process_circuit, args=(c,ID_KEY,ID_STATUS,ID_SOCK,ned)).start()
         elif "data" == v:
+            print "data"
             Process(target=process_data, args=(c,ID_SOCK,ned)).start()
 
 

### 2014-03-16 server/Client.py
1 length circuits seem to work

@@ -5,6 +5,7 @@ import socket
 import threading
 import sys
 import ast
+import random
 
 lock = threading.RLock()
 host = socket.gethostname()
@@ -50,12 +51,19 @@ def sendData(data):
         tsock.send("data"+data+"END")
     tsock.close()
 
-def generateCircuit(n, enduser, message, keys, svrkeys):
+def generateCircuit(n, enduser, message, keys, online, svrkeys):
     if enduser not in keys.keys():
         return None
 
     #first encrypt for the intended recipient
     ct = encrypt(message, keys[enduser][1], keys[enduser][0], enduser, svrkeys)
+
+    length = 1
+    while length < n:
+        user = random.choose(online)
+        pair = keys[user]
+        ct = encrypt(ct, pair[1], pair[0], user, svrkeys)
+
     return ct
 
 
@@ -68,6 +76,7 @@ def user(name, p, msgs, ned):
     the origin of a message
     """
     keys = {}
+    online = []
     s = socket.socket()
     port = 8000
     s.connect((host,port))
@@ -105,13 +114,14 @@ def user(name, p, msgs, ned):
 
         if words == ":ls":
             s.send(words)
-            print "Server: " + s.recv(1024)
+            online = readFromSocketUntil(s)
+            print "Online users: " + online
         if words.startswith(":send"):
             words = words[6:]
             index = words.find(" ")
             target,msg = words[:index],words[index+1:]
             
-            circuit = generateCircuit(5, target, "msg"+name+": "+msg, keys, svrkeys)
+            circuit = generateCircuit(1, target, "msg"+name+": "+msg, keys, online, svrkeys)
             if circuit == None:
                 print "Do not have that user's key, try :ks"
             else:

### 2014-03-16 server/Server.py

@@ -32,7 +32,7 @@ def process_client(c, ID_KEY, ID_STATUS, ID_SOCK, ned):
             print c_id + " sent a new public key " + v
         elif v.startswith(":ls"):
             print "list requested, sending: %s" % ID_STATUS
-            c.send("%s" % filter(lambda x: ID_STATUS.get(x, False)  == True,ID_STATUS.keys()))
+            c.send("%sEND" % filter(lambda x: ID_STATUS.get(x, False)  == True,ID_STATUS.keys()))
         elif v.startswith(":ks"):
             print "keys requested, sending: %s" % ID_KEY
             c.send("%sEND" % ID_KEY)

### 2014-03-16 server/Client.py
It works

@@ -60,9 +60,10 @@ def generateCircuit(n, enduser, message, keys, online, svrkeys):
 
     length = 1
     while length < n:
-        user = random.choose(online)
+        user = random.choice(online)
         pair = keys[user]
         ct = encrypt(ct, pair[1], pair[0], user, svrkeys)
+        length += 1
 
     return ct
 
@@ -114,14 +115,14 @@ def user(name, p, msgs, ned):
 
         if words == ":ls":
             s.send(words)
-            online = readFromSocketUntil(s)
-            print "Online users: " + online
+            online = ast.literal_eval(readFromSocketUntil(s))
+            print "Online users: %s" % online
         if words.startswith(":send"):
             words = words[6:]
             index = words.find(" ")
             target,msg = words[:index],words[index+1:]
             
-            circuit = generateCircuit(1, target, "msg"+name+": "+msg, keys, online, svrkeys)
+            circuit = generateCircuit(2, target, "msg"+name+": "+msg, keys, online, svrkeys)
             if circuit == None:
                 print "Do not have that user's key, try :ks"
             else:

### 2014-03-16 server/Server.py

@@ -67,24 +67,25 @@ def process_data(c, ID_SOCK, ned):
     Put the encrypted portion of the message into the SOCK dictionary
     for that user
     """
-    with lock:
-        #read data until END
-        d = ""
-        block = ""
-        while block.find("END") == -1:
-            block = str(c.recv(64))
-            d += block
-        d += block
-        d = d[:d.find("END")]
 
-        #reformat to integer list
-        d = pickle.loads(d)
-        d = rsa.decrypt(d, ned[0], ned[2], 15)
-        d = d.split("||")
+    #read data until END
+    d = ""
+    block = ""
+    while block.find("END") == -1:
+        block = str(c.recv(64))
+        d += block
+    d += block
+    d = d[:d.find("END")]
+
     
-        name = d[0].lstrip("x")
-        #write result to socket for another user to await transfer
-        ID_SOCK[name] = d[1] 
+    #reformat to integer list
+    d = pickle.loads(d)
+    d = rsa.decrypt(d, ned[0], ned[2], 15)
+    d = d.split("||")
+    
+    name = d[0].lstrip("x")
+    #write result to socket for another user to await transfer
+    ID_SOCK[name] = d[1] 
     c.close()
 
 def main():
@@ -97,7 +98,7 @@ def main():
     ID_SOCK = manager.dict()
 
     s = socket.socket()
-    s.setsockopt(socket.SOL_SOCKET, socket.SO_REUSEADDR, 1)
+
     hostname = socket.gethostname()
     port = 8000
     s.bind(('',port))
@@ -112,7 +113,6 @@ def main():
         elif "circ" == v:
             Process(target=process_circuit, args=(c,ID_KEY,ID_STATUS,ID_SOCK,ned)).start()
         elif "data" == v:
-            print "data"
             Process(target=process_data, args=(c,ID_SOCK,ned)).start()
 
 

### 2014-03-16 server/Client.py
FIxed the problem with feeding pickled data through a socket

@@ -147,7 +147,7 @@ def decrypt(data,ned):
     """
     decrypt if you know what I mean wink wink nudge nudge
     """
-    data = pickle.loads(data)
+    data = pickle.loads(str(data))
 #    data = map(int,data.split(":"))
     return rsa.decrypt(data, ned[0], ned[2], 15)
 

### 2014-03-16 server/Server.py

@@ -77,9 +77,10 @@ def process_data(c, ID_SOCK, ned):
     d += block
     d = d[:d.find("END")]
 
+    print "Process '%s'" % d
     
     #reformat to integer list
-    d = pickle.loads(d)
+    d = pickle.loads(str(d))
     d = rsa.decrypt(d, ned[0], ned[2], 15)
     d = d.split("||")
     

### 2014-03-17 server/Client.py
Broken stuff

@@ -1,4 +1,4 @@
-import pickle
+import cPickle as pickle
 import rsa
 from multiprocessing import Process, Manager
 import socket

### 2014-03-17 server/Server.py

@@ -1,4 +1,5 @@
-import pickle
+import signal
+import cPickle as pickle
 import rsa
 from multiprocessing import Process, Manager
 import socket
@@ -89,14 +90,31 @@ def process_data(c, ID_SOCK, ned):
     ID_SOCK[name] = d[1] 
     c.close()
 
-def main():
+def main(data):
+    """
+    Launches the server with given set of keys (data)
+    """
     ned = rsa.newKey(10**100,10**101,50)
     print "Keys\nn = %s\ne = %s\nd = %s\n" % (ned[0],ned[1],ned[2])
 
     manager = Manager()
     ID_KEY = manager.dict()
+    ID_KEY.update(data) #get saved data
     ID_STATUS = manager.dict()
     ID_SOCK = manager.dict()
+
+    #define an interupt catcher to save data (doesnt work)
+    def signal_handler(signal, frame):
+        print('Saving data')
+        with lock:
+            with open('serverdata.pkl', 'wb') as f:
+                temp = {}
+                print "%s" % ID_KEY
+                for key in iter(ID_KEY.keys()):
+                    print key
+                pickle.dump( temp, f ) #save keys on edit
+        sys.exit(0)
+    signal.signal(signal.SIGINT, signal_handler)
 
     s = socket.socket()
 
@@ -105,6 +123,7 @@ def main():
     s.bind(('',port))
     s.listen(5)
     
+    #listen for incoming connections and start a thread based on what kind it is
     while True:
         c, addr =  s.accept()
         c.send("init")
@@ -118,4 +137,11 @@ def main():
 
 
 if __name__ == "__main__":
-    main()
+    try:
+        with open('serverdata.pkl', 'rb') as f:
+            data = pickle.load(f)
+            main(data)
+    except:
+        print "Data not found"
+        main({})
+        

### 2014-03-17 server/Server.py
Saves correctly now

@@ -1,3 +1,4 @@
+import ast
 import signal
 import cPickle as pickle
 import rsa
@@ -108,10 +109,7 @@ def main(data):
         print('Saving data')
         with lock:
             with open('serverdata.pkl', 'wb') as f:
-                temp = {}
-                print "%s" % ID_KEY
-                for key in iter(ID_KEY.keys()):
-                    print key
+                temp = ast.literal_eval(str(ID_KEY))
                 pickle.dump( temp, f ) #save keys on edit
         sys.exit(0)
     signal.signal(signal.SIGINT, signal_handler)
@@ -140,8 +138,8 @@ if __name__ == "__main__":
     try:
         with open('serverdata.pkl', 'rb') as f:
             data = pickle.load(f)
-            main(data)
     except:
         print "Data not found"
-        main({})
-        
+        data = {}
+
+    main(data)

### 2014-03-17 paper.tex
fixed corrections

@@
 In this paper we present a centralized anonymity system that uses a single, untrusted central server, adapting decentralized peer-to-peer (P2P) protocols to work in this context, and combine these with Computational Private Information Retrieval (CPIR) to enable low-latency, low-overhead anonymous communication.
-The primary reason behind a centeral server is to have a browser based service which needs a server to route for a pseudo-P2P network.
+The primary reason behind a central server is to have a browser based service which needs a server to route for a pseudo-P2P network.
 
@@
 Traditional cryptography hides the message being sent from one party to another.
-This is useful for many purposes but there is an important aspect of your communication that is freely availble to anyone observing the transfer: the connection between sender and recipient.
+This is useful for many purposes, but there is an important aspect of your communication that is freely availble to anyone observing the transfer: the connection between sender and recipient.
 
@@
 Our message system is accessed via the browser, allowing a person to browse to one central location and conveniently use this service, rather than using an external program for anonymity as with existing P2P services.
-The central server is acts as an intermediary and facilitator for the network of peers using it.
+The central server acts as an intermediary and facilitator for the network of peers using it.
 The peers are used to obsfucate who is sending messages to whom, allowing the clients to maintain anonymity and message security, in as close to real time as possible.
@@
 
-The anonymity mixes provide depends on many factors and was thoroughly analyzed by Serjantov in~\cite{trickle02}.
+The anonymity mixes provide depends on many factors and was thoroughly analyzed by Serjantov~\cite{trickle02}.
 In our system we use peers in the network as mixes, and will analyze their security using the known attacks that Serjantov presents (See Section~\ref{sec:PeersAsMixes} for a more in depth discussion).
@@
 
-With a single server, PIR was discovered to still be possible, however.
+It was discovered that PIR is possible with a single server.
 Computational PIR (first introduced by Chor \cite{CPIR}) uses computationally difficult mechanisms to prevent a server hosting a single database from learning which records users retrieve from it.
@@
 Each successive party receives a message and an ID to forward that message to, and only that party can read its message.
-Importantly, any Penguin or Proletariat without collusion from Surge doesn't gain any information about the source or destination of the message it's passing along.
+Any Penguin or Proletariat without collusion from Surge doesn't gain any information about the source or destination of the message it's passing along.
 
@@
 \subsection{Security Flaws}
-Here we'll perform a simplified analysis of the security flaws of the basic, na\"ive system described so far. 
+Here we will perform a simplified analysis of the security flaws of the basic, na\"ive system described so far. 
 Let $P_{AB}$ be the probability that Alice sent a given message that was delivered to to Bob. 
@@
 MixMinion \cite{minion-design} solves these problems by having a small group of directory servers that only update nightly, having servers sign each other's directories, and ensuring that users download entire directories.
-These solutions are not feasible in our case since the set of online users is constantly in flux, and is likely to be too large to be sent to every user.
+This solution is not feasible because set of online users is constantly changing.
+Sending the entire user list to every user each time someone logs on or off is infeasable.
 Tor \cite{tor-design} likewise has a small number of trusted directory servers that share infrequently updated, signed directories.
@@
 If Surge doesn't exclude non-colluding peers from the online list, however, Alice will inevitably include some of them in her chosen circuits.
-Since Surge doesn't know that Alice and Bob are communicating beforehand, he is forced to either include or exclude all non-colluding peers from the online-peers database as a whole.
+Since Surge doesn't know that Alice and Bob are communicating beforehand, he is forced to either include or exclude all non-colluding peers from the online-peers database~as~a~whole.
 
@@
 If Surge is willing to allow Bob to learn that he's lying about public keys, Surge can share a fake public key with the world and masquerade as Bob, intercepting all initial messages sent to him and potentially learning the identities of Bob's associates.
-Worse, he could masquerade only when he knows Bob is offline, while lying and saying that Bob is actually online.
+Worse, he could masquerade as Bob when he knows Bob is offline.
 

### 2014-03-17 server/Client.py
Comments

@@ -11,6 +11,10 @@ lock = threading.RLock()
 host = socket.gethostname()
 
 def readFromSocketUntil(s, signal="END"):
+    """
+    Takes a socket s and a terminating signal to listen for
+    and reads all data up until the signal
+    """
     data_from_server = ""
     block = ""
     while block.find(signal) == -1:
@@ -43,6 +47,9 @@ def encrypt(message, n, e, userId, svrkey):
     return msg
     
 def sendData(data):
+    """
+    Send data to the server without using the same socket as the user input
+    """
     tsock = socket.socket()
     port = 8000
     tsock.connect((host,port))
@@ -52,12 +59,17 @@ def sendData(data):
     tsock.close()
 
 def generateCircuit(n, enduser, message, keys, online, svrkeys):
+    """
+    Generates a circuit to send a message through given an end recepient
+    """
+
     if enduser not in keys.keys():
         return None
 
     #first encrypt for the intended recipient
     ct = encrypt(message, keys[enduser][1], keys[enduser][0], enduser, svrkeys)
 
+    #layer on more encryptions to more users based on the desired circuit length
     length = 1
     while length < n:
         user = random.choice(online)
@@ -113,10 +125,12 @@ def user(name, p, msgs, ned):
 
             print "Downloaded " + str(len(keys.keys()))  + " keys"
 
+        #request a list of users from the server
         if words == ":ls":
             s.send(words)
             online = ast.literal_eval(readFromSocketUntil(s))
             print "Online users: %s" % online
+        #send a message to the server
         if words.startswith(":send"):
             words = words[6:]
             index = words.find(" ")
@@ -127,17 +141,18 @@ def user(name, p, msgs, ned):
                 print "Do not have that user's key, try :ks"
             else:
                 sendData(circuit)
-
+        #send the server a key
         if words.startswith(":setkey"):
             with lock:
                 s.send(":setkey " + str(ned[1])+"n"+str(ned[0]))
             print "Keys: %s" % s.recv(1024)
+        #generate a new keypair
         if words.startswith(":genkey"):
             with lock:
                 ned = rsa.newKey(10**100,10**101,50)
             print "n = %s\ne = %s\nd = %s\n" % (ned[0],ned[1],ned[2])
             with open('%s.keys' % name, 'w') as f:
-                f.write("%d\n%s\n%s\n" %(ned[0],ned[1],ned[2]))
[…]

### 2014-03-17 server/Server.py

@@ -1,3 +1,8 @@
+##################
+# Blow ship server
+#################
+#Proof of concept, not feature complete.
+
 import ast
 import signal
 import cPickle as pickle
@@ -11,6 +16,9 @@ import sys
 lock = threading.RLock()
 
 def process_client(c, ID_KEY, ID_STATUS, ID_SOCK, ned):
+    """
+    This function servs as a thread that listens for user input
+    """
     c_id = c.recv(1024)
     print c_id + " logged in"
     with lock:
@@ -19,22 +27,27 @@ def process_client(c, ID_KEY, ID_STATUS, ID_SOCK, ned):
 
     c.send(str(ned[1])+"n"+str(ned[0]))
 
+    #listen for user input and respond if need be
     running = True
     while running:
         v = c.recv(1024)
+        #end user wishes to log out
         if v == ":bye":
             print c_id + " logged out"
             running = False
             c.send("bye")
+        #user is sending their public key and n value
         elif v.startswith(":setkey"):
             v = v[7:]
             with lock:
                 ID_KEY[c_id] = v
             c.send("reset key to: " + v)
             print c_id + " sent a new public key " + v
+        #user wants to know who is online
         elif v.startswith(":ls"):
             print "list requested, sending: %s" % ID_STATUS
             c.send("%sEND" % filter(lambda x: ID_STATUS.get(x, False)  == True,ID_STATUS.keys()))
+        #user wants to know all other users keys (including their own)
         elif v.startswith(":ks"):
             print "keys requested, sending: %s" % ID_KEY
             c.send("%sEND" % ID_KEY)
@@ -47,8 +60,16 @@ def process_client(c, ID_KEY, ID_STATUS, ID_SOCK, ned):
 
 
 def process_circuit(c, ID_KEY, ID_STATUS, ID_SOCK, ned):
+    """
+    This thread moniters
+    """
     c_id = c.recv(1024)
 
+    #every second check if there is a message for user c_id
+    #if so send it to them through their circuit socket
+    #they will recieve decrypt the message and either
+    #1) Keep it if it belongs to them
+    #2) Send it back to the server through a new data connection if they cannot read it
     running = True
     while running:
         time.sleep(1)
@@ -79,8 +100,6 @@ def process_data(c, ID_SOCK, ned):
     d += block
     d = d[:d.find("END")]
 
-    print "Process '%s'" % d
-    
     #reformat to integer list
     d = pickle.loads(str(d))
     d = rsa.decrypt(d, ned[0], ned[2], 15)
[…]

### 2014-03-17 server/Client.py
KDLFJLKDSJ

@@ -136,6 +136,7 @@ def user(name, p, msgs, ned):
             index = words.find(" ")
             target,msg = words[:index],words[index+1:]
             
+            #first arg is the length of the circuit to generate 2 is risky causes crashes sometimes. 1 seems to be safe
             circuit = generateCircuit(2, target, "msg"+name+": "+msg, keys, online, svrkeys)
             if circuit == None:
                 print "Do not have that user's key, try :ks"

### 2014-03-17 paper.tex
Email
Updates

@@
 \section{The Na\"ive Protocol}
+\label{sec:naive}
 Many of the developed P2P techniques can be adapted by using a pseudo-P2P protocol, having peers communicate with each other indirectly through the central server.
@@
 \subsection{Basic Protocol}
+\label{sec:basic}
 Assume that Alice has obtained Bob's public key and unique ID while maintaining her anonymity.
@@
 
+ In mix systems, it is important that messages are padded to be the same length to prevent message correlation \cite{chaum-mix}.
+Without this, Surge can inspect the size of messages sent to a peer and gain information about which incoming messages might be outgoing messages.
+
 \subsection{Anonymity inside The Fort} 
+\label{sec:thefort}
 Using this improved pseudo-P2P message system, we will analyze the security of Alice sending a single message to Bob when Surge colludes with Penguins to form The Fort.
@@
 \subsection{Likelihood of the worst-case}
+\label{sec:worstcase}
 We'd like to know how likely the worst-case ($p(P_{AB} > \gamma)$) scenario is given the circuit length chosen by Alice.
@@
 
-\section{Applying PIR to Routing}
-\subsection{PIR usage}
-An obvious way to utilize PIR for anonymous communication is as a ``Dead Drop''.
-If we have a PIR server Charlie, Alice could write her messages to block $i$ in Charlie's PIR database, then Bob could request block $i$ anonymously.
-This could enable us to increase the size of Alice's anonymity set (retaining a uniform distribution of probabilities, as well) while reducing our circuit length significantly.
-
-\subsection{PIR issues}
-There are, however, several problems with this configuration.
-
-First, Alice must communicate Charlie's ID and $i$ to Bob anonymously. This could happen via the pseudo-P2P protocol as above.
-
-Second, Alice and Bob both start talking to Charlie around the same time.
-If Charlie suspects Alice and Bob are talking to each other, he can easily create a fake PIR database for all of Alice's inserts and all of Bob's retrievals, and if they continue to communicate normally he has discovered a connection.
-
-\section{Offline delivery of messages}
- PYNCHON GATE
-
 \section{Future Work}
 \begin{description}
-\item[Pseudonymity.] Allow for parties to communicate securely without knowing each other's identities.
-Currently our system relies heavily (at least when a person first enters the network) on the fact that the person initiating the communication knows the person's key with whom he wants to communciate.
+\item[Pseudonymity and offline message delivery.] We would like to allow for parties to communicate securely without knowing each other's identities.
+Currently our system relies heavily on a peer knowing the public key of the final recipient of their message.
+
+To obtain both pseudonymity and offline message delivery, we could employ a Pynchon Gate as developed by Sassaman \cite{sassaman:wpes2005}.
+We would need to use CPIR instead of ITPIR since we are employing a single central server, but the same principle allowing for pseudonymity applies.
 
@@
 
-\item[Resilience.] Long circuits will inevitably lead to them breaking down due to people going offline intermittently. We need efficient ways of dealing with this.
+\item[Peer Storage.]
+  Ultimately it will be necessary for the system to offer storage to peers using the network.
+This will allow peers to store their keyring on the central server, as well as mail that they have already received.
+The data stored by the server would be encrypted entirely by the peer, ensuring that the server can't obtain the contents of their mail, which keys they trust, etc.
 
-\item[Analyze performance of using PIR] a
+\item[Applying PIR to Routing]
+We could potentially reduce the length of circuits by using PIR databases as a hop in the chain.
+An obvious way to utilize PIR for anonymous communication is as a ``Dead Drop''.
+If we have a PIR server Charlie, Alice could write her messages to block $i$ in Charlie's PIR database, then Bob could request block $i$ anonymously.
+This could enable us to increase the size of Alice's anonymity set (retaining a uniform distribution of probabilities, as well) while reducing our circuit length significantly.
 
-\item[Final summary/review of protocol]a
+There are, however, several problems with this configuration.
 
-\item[Final security analysis of protocol]a
+First, Alice must communicate Charlie's ID and $i$ to Bob anonymously. This could happen via the pseudo-P2P protocol as above.
 
-\item[User storage for data, keys, mail, etc]a
+Second, Alice and Bob both start talking to Charlie around the same time.
+If Charlie suspects Alice and Bob are talking to each other, he can easily create a fake PIR database for all of Alice's inserts and all of Bob's retrievals, and if they continue to communicate normally he has discovered a connection.
 
-\item[Analyze reusing people in circuits]a
+We would like to develop this strategy further in the future - at present, it is not efficient or secure enough to employ.
+\end{description}
 
-\item[Message Padding]a
+\section{Summary}
+ We've summarized some of the key points of the protocol in Figure~\ref{fig:keypoints}, and give a broad outline of the protocol below:
 
-\item[Clarify why cover traffic is needed]a
-\end{description}
+\begin{figure*}[scale=0.7]
+\includegraphics{summary.eps}
+\caption{Key Points of Protocol Summary}
+\label{fig:keypoints}
+\end{figure*}
+
+\begin{enumerate}
+
+  \item The central server houses two Private Information Retrieval databases: one containing all online users, and one containing all user's keys.
+Peers can only communicate indirectly through the server, and always do so with encrypted messages.
+  \item Messages are sent using the basic structure from Section~\ref{sec:basic}, using layers of public key encryption to pass through the server and peers in an alternating fashion. 
+  \item Circuits through which messages are sent are chosen by the peer who wishes to send a message.
+These circuits are chosen randomly from the server's PIR database of online users.
+The circuit length can be chosen as $log(N)$ where $N$ is the number of online users, as discussed in Section~\ref{sec:thefort}, or according to acceptable risk as discussed in Section~\ref{sec:worstcase}.
+  \item Peers act as relays for other peers, but don't know the true destination of messages they decrypt and relay back to the server.
+It's important that since peers act as mixes (Section~\ref{sec:PeersAsMixes}), they always wait until they receive two messages before they forward them onward, that messages are always padded to a fixed length, and that peers always generate 1 fake message as cover traffic, using a circuit length of at least 1 hop.
+  \item Peers need to audit their public keys by requesting that other peers request their public key and relay it back to them, to make man-in-the-middle attacks more challenging.
+Additionally, peers need to store the retrieved keys of other peers in order to detect discrepancies that could indicate an attack.
+Keys should be signed and given trust levels as in PGP to further mitigate this risk.
+\end{enumerate}
+
 \section{Conclusion}
-Conclusion words here about our network which is basically whatever we have in the introduction
+In this paper, we have introduced a system for sending anonymous messages via a central server with low-latency.
+This system is designed to prevent the correlation between the sender and receiver of messages, using an adaption of P2P protocols to the central server setting.
+We analyzed the probabilistic security of using peers as 2-threshhold mixes given different circuit lengths.
 
+We showed that malicious peers on their own only have the power to delay or prevent message delivery.
+When colluding with the central server, peers can only reduce a sender's security probabilistically.
+This risk can be mitigated by circuit length.
+To prevent attacks by the central server using its databases and knowledge of keys, we have suggested the use of a web of trust, auditing, and key storage.
 \newpage
-
+\begin{figure*}
 \bibliography{paper.bib}
 \bibliographystyle{unsrt}
+\end{figure*}
 \end{document}
